---
title: "log_log_PNC_PFNs_normative"
author: "Kevin Sun"
date: "`10/31/2025`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
library(readr)
library(sjPlot)
library(mgcv)
```

#Import areas and demographics
```{r}

PNC_TC_and_PFNs_network_areas <- read.csv("../../Inputs/PNC_summary_PFNs.csv") # n = 1482
colnames(PNC_TC_and_PFNs_network_areas)[1] <- "participant_id"
colnames(PNC_TC_and_PFNs_network_areas)[3] <- "PFN1_soft_parcel_normed"
colnames(PNC_TC_and_PFNs_network_areas)[4] <- "PFN2_soft_parcel_normed"
colnames(PNC_TC_and_PFNs_network_areas)[5] <- "PFN3_soft_parcel_normed"
colnames(PNC_TC_and_PFNs_network_areas)[6] <- "PFN4_soft_parcel_normed"
colnames(PNC_TC_and_PFNs_network_areas)[7] <- "PFN5_soft_parcel_normed"
colnames(PNC_TC_and_PFNs_network_areas)[8] <- "PFN6_soft_parcel_normed"
colnames(PNC_TC_and_PFNs_network_areas)[9] <- "PFN7_soft_parcel_normed"
colnames(PNC_TC_and_PFNs_network_areas)[10] <- "PFN8_soft_parcel_normed"
colnames(PNC_TC_and_PFNs_network_areas)[11] <- "PFN9_soft_parcel_normed"

PNC_demos <- read.csv("../../Inputs/filtered_demo_PNC.csv") #n = 1332
PNC_all <- merge(PNC_TC_and_PFNs_network_areas,PNC_demos,by="participant_id") # n = 1332

write_csv(PNC_all,paste0("../../Inputs/PNC_filtered_all.csv"))

PFN_names <- c("DM-B", "SM-foot", "FP-A", "SM-face", "DA-post", "VS-peri", "Salience", "Language", "CingOp", "VS-cent", "SM-lh", "DM-A", "SM-rh", "DA-ant", "ParMem", "Auditory", "FP-B")

```

#Factorize sex
```{r}
PNC_all$sex <- factor(PNC_all$sex)
```

#Get statistics of areas
```{r}
dout <- "../../Results/Area_stats"
dir.create(dout)

PFN_area_stats <- matrix(0,17,2)

for (net in c(1:17)) {
  PFN_area_stats[net,1] <- mean(PNC_all[,net+2])
  PFN_area_stats[net,2] <- sd(PNC_all[,net+2])
}
PFN_names <- c("PFN1", "PFN2", "PFN3", "PFN4", "PFN5", "PFN6", "PFN7", "PFN8", "PFN9", "PFN10", "PFN11", "PFN12", "PFN13", "PFN14", "PFN15", "PFN16", "PFN17")

PFN_area_stats <- data.frame(Network = PFN_names, area_mean = PFN_area_stats[,1], area_SD = PFN_area_stats[,2])

write_csv(PFN_area_stats,paste0(dout,"/PNC_PFNs_area_stats.csv"))
```

### Bar plot of PFN area stats:
```{r}
mean_area <- PFN_area_stats[,2]
sd_area   <- PFN_area_stats[,3]

# Base data frame with identity preserved
data <- data.frame(
  EffectSizes = as.numeric(mean_area),
  SD          = as.numeric(sd_area),
  Network     = 1:17
)

# ---- SORT BY MEAN AREA (ascending) ----
data <- data[order(data$EffectSizes), ]

# Make Network a factor in sorted order
data$Network <- factor(data$Network, levels = data$Network)

# Colors tied to original network numbers
BorderColor <- c("#E76178", "#7499C2", "#F5BA2E", "#7499C2", "#00A131",
                 "#AF33AD", "#E443FF", "#E76178", "#E443FF", "#AF33AD",
                 "#7499C2", "#E76178", "#7499C2", "#00A131", "#F5BA2E", 
                 "#4E31A8", "#F5BA2E")

LineType <- rep("solid", 17)

# Get original network indices in sorted order
network_idx <- as.numeric(as.character(data$Network))

Fig <- ggplot(data, aes(x = Network, y = EffectSizes)) +
  geom_bar(stat = "identity",
           fill   = BorderColor[network_idx],
           colour = BorderColor[network_idx],
           linetype = LineType[network_idx],
           width = 0.8) +
  # ---- BLACK ERROR BARS ----
  geom_errorbar(aes(ymin = EffectSizes - SD, ymax = EffectSizes + SD),
                width = 0.2,
                size = 0.9,
                color = "black") +
  labs(title = "PFN Area Mean + SD",
       x = "Networks",
       y = "Surface Area (mm2)") +
  theme_classic() +
  theme(
    # REMOVE LEGEND
    legend.position = "none",
    plot.title = ggtext::element_markdown(size = 25, hjust = 0.5),
    axis.text.x = ggtext::element_markdown(size = 25,
                                           color = BorderColor[network_idx],
                                           angle = 45, hjust = 1),
    axis.text.y = ggtext::element_markdown(size = 25, color = "black"),
    axis.title  = ggtext::element_markdown(size = 25)
  ) +
  scale_y_continuous(limits = c(0, 21000))
Fig
ggsave("../../Results/Area_stats/PNC_PFNs_area_stats_plot_sorted.png",
       width = 19, height = 16, dpi = 600, units = "cm")
```

## log-log models including age spline
```{r}
dout <- "../../Results/PNC_PFN_Age"
dir.create(dout)

summary(gam(log(PFN1_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML"))
PFN1_gam<-gam(log(PFN1_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML")
#tab_model(PFN1_gam,pred.labels = c("Intercept","log TC Area","Sex","Euler Number","Median FD","Age Spline"),dv.labels=c("log PFN1"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = paste(dout,"/PNC_PFNs_PFN1_area_TC_area_age_cov_REML.doc", sep = ""))

summary(gam(log(PFN2_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML"))
PFN2_gam<-gam(log(PFN2_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML")
#tab_model(PFN2_gam,pred.labels = c("Intercept","log TC Area","Sex","Euler Number","Median FD","Age Spline"),dv.labels=c("log PFN2"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = paste(dout,"/PNC_PFNs_PFN2_area_TC_area_age_cov_REML.doc", sep = ""))

summary(gam(log(PFN3_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML"))
PFN3_gam<-gam(log(PFN3_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML")
#tab_model(PFN3_gam,pred.labels = c("Intercept","log TC Area","Sex","Euler Number","Median FD","Age Spline"),dv.labels=c("log PFN3"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = paste(dout,"/PNC_PFNs_PFN3_area_TC_area_age_cov_REML.doc", sep = ""))

summary(gam(log(PFN4_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML"))
PFN4_gam<-gam(log(PFN4_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML")
#tab_model(PFN4_gam,pred.labels = c("Intercept","log TC Area","Sex","Euler Number","Median FD","Age Spline"),dv.labels=c("log PFN4"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = paste(dout,"/PNC_PFNs_PFN4_area_TC_area_age_cov_REML.doc", sep = ""))

summary(gam(log(PFN5_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML"))
PFN5_gam<-gam(log(PFN5_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML")
#tab_model(PFN5_gam,pred.labels = c("Intercept","log TC Area","Sex","Euler Number","Median FD","Age Spline"),dv.labels=c("log PFN5"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = paste(dout,"/PNC_PFNs_PFN5_area_TC_area_age_cov_REML.doc", sep = ""))

summary(gam(log(PFN6_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML"))
PFN6_gam<-gam(log(PFN6_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML")
#tab_model(PFN6_gam,pred.labels = c("Intercept","log TC Area","Sex","Euler Number","Median FD","Age Spline"),dv.labels=c("log PFN6"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = paste(dout,"/PNC_PFNs_PFN6_area_TC_area_age_cov_REML.doc", sep = ""))

summary(gam(log(PFN7_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML"))
PFN7_gam<-gam(log(PFN7_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML")
#tab_model(PFN7_gam,pred.labels = c("Intercept","log TC Area","Sex","Euler Number","Median FD","Age Spline"),dv.labels=c("log PFN7"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = paste(dout,"/PNC_PFNs_PFN7_area_TC_area_age_cov_REML.doc", sep = ""))

summary(gam(log(PFN8_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML"))
PFN8_gam<-gam(log(PFN8_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML")
#tab_model(PFN8_gam,pred.labels = c("Intercept","log TC Area","Sex","Euler Number","Median FD","Age Spline"),dv.labels=c("log PFN8"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = paste(dout,"/PNC_PFNs_PFN8_area_TC_area_age_cov_REML.doc", sep = ""))

summary(gam(log(PFN9_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML"))
PFN9_gam<-gam(log(PFN9_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML")
#tab_model(PFN9_gam,pred.labels = c("Intercept","log TC Area","Sex","Euler Number","Median FD","Age Spline"),dv.labels=c("log PFN9"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = paste(dout,"/PNC_PFNs_PFN9_area_TC_area_age_cov_REML.doc", sep = ""))

summary(gam(log(PFN10_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML"))
PFN10_gam<-gam(log(PFN10_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML")
#tab_model(PFN10_gam,pred.labels = c("Intercept","log TC Area","Sex","Euler Number","Median FD","Age Spline"),dv.labels=c("log PFN10"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = paste(dout,"/PNC_PFNs_PFN10_area_TC_area_age_cov_REML.doc", sep = ""))

summary(gam(log(PFN11_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML"))
PFN11_gam<-gam(log(PFN11_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML")
#tab_model(PFN11_gam,pred.labels = c("Intercept","log TC Area","Sex","Euler Number","Median FD","Age Spline"),dv.labels=c("log PFN11"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = paste(dout,"/PNC_PFNs_PFN11_area_TC_area_age_cov_REML.doc", sep = ""))

summary(gam(log(PFN12_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML"))
PFN12_gam<-gam(log(PFN12_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML")
#tab_model(PFN12_gam,pred.labels = c("Intercept","log TC Area","Sex","Euler Number","Median FD","Age Spline"),dv.labels=c("log PFN12"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = paste(dout,"/PNC_PFNs_PFN12_area_TC_area_age_cov_REML.doc", sep = ""))

summary(gam(log(PFN13_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML"))
PFN13_gam<-gam(log(PFN13_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML")
#tab_model(PFN13_gam,pred.labels = c("Intercept","log TC Area","Sex","Euler Number","Median FD","Age Spline"),dv.labels=c("log PFN13"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = paste(dout,"/PNC_PFNs_PFN13_area_TC_area_age_cov_REML.doc", sep = ""))

summary(gam(log(PFN14_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML"))
PFN14_gam<-gam(log(PFN14_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML")
#tab_model(PFN14_gam,pred.labels = c("Intercept","log TC Area","Sex","Euler Number","Median FD","Age Spline"),dv.labels=c("log PFN14"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = paste(dout,"/PNC_PFNs_PFN14_area_TC_area_age_cov_REML.doc", sep = ""))

summary(gam(log(PFN15_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML"))
PFN15_gam<-gam(log(PFN15_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML")
#tab_model(PFN15_gam,pred.labels = c("Intercept","log TC Area","Sex","Euler Number","Median FD","Age Spline"),dv.labels=c("log PFN15"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = paste(dout,"/PNC_PFNs_PFN15_area_TC_area_age_cov_REML.doc", sep = ""))

summary(gam(log(PFN16_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML"))
PFN16_gam<-gam(log(PFN16_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML")
#tab_model(PFN16_gam,pred.labels = c("Intercept","log TC Area","Sex","Euler Number","Median FD","Age Spline"),dv.labels=c("log PFN16"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = paste(dout,"/PNC_PFNs_PFN16_area_TC_area_age_cov_REML.doc", sep = ""))

summary(gam(log(PFN17_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML"))
PFN17_gam<-gam(log(PFN17_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML")
#tab_model(PFN17_gam,pred.labels = c("Intercept","log TC Area","Sex","Euler Number","Median FD","Age Spline"),dv.labels=c("log PFN17"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = paste(dout,"/PNC_PFNs_PFN17_area_TC_area_age_cov_REML.doc", sep = ""))

```

# Get significance of beta scaling term via Wald test
```{r}
dout <- "../../Results/PNC_PFN_Age"

log_log_results <- matrix(0,17,2)

for (net in c(1:17)) {
  beta <- summary(get(paste0("PFN",net,"_gam")))$p.table["log(TC_area)", "Estimate"]
  SE <- summary(get(paste0("PFN",net,"_gam")))$p.table["log(TC_area)", "Std. Error"]
  z_val <- (beta - 1) / SE # Null is beta = 1 (isometry, linear scaling)
  #df <- df.residual(get(paste0("PFN",net,"_gam")))
  log_log_results[net,1] <- beta
  log_log_results[net,2] <- 2 * (1 - pnorm(abs(z_val))) #Wald test
}

pvals_bonf <- p.adjust(log_log_results[,2], method = "bonf")
#PFN_names <- c("PFN1", "PFN2", "PFN3", "PFN4", "PFN5", "PFN6", "PFN7", "PFN8", "PFN9", "PFN10", "PFN11", "PFN12", "PFN13", "PFN14", "PFN15", "PFN16", "PFN17")
log_log_wald_bonf <-  data.frame(PFN = PFN_names, beta = log_log_results[,1], pvals_bonf = pvals_bonf)

#write_csv(log_log_wald_bonf,paste0(dout,"/PNC_PFNs_log_log_summary_results_bonf_REML_netnames.csv"))
```

# Test unimodal vs heteromodal allometry as described in Anderson et al. 2020
```{r}
library(emmeans)

dout <- "../../Results/PNC_PFN_Age"
dir.create(dout, showWarnings = FALSE, recursive = TRUE)

mode_group <- factor(
  c(2,1,2,1,2,1,2,2,2,1,1,2,1,2,2,1,2),
  levels = c(1, 2),
  labels = c("Unimodal", "Heteromodal")
)

dat <- data.frame(
  PFN = paste0("PFN", 1:17),
  beta = log_log_results[, 1],
  mode_group = mode_group
)

tt <- t.test(beta ~ mode_group, data = dat)

group_summary <- dat %>%
  group_by(mode_group) %>%
  summarise(
    n = n(),
    M = mean(beta, na.rm = TRUE),
    SD = sd(beta, na.rm = TRUE),
    .groups = "drop"
  )

ttest_summary <- data.frame(
  outcome = "beta",
  test = "Welch two-sample t-test",
  comparison = "Heteromodal vs Unimodal",
  mean_heteromodal = group_summary$M[group_summary$mode_group == "Heteromodal"],
  sd_heteromodal = group_summary$SD[group_summary$mode_group == "Heteromodal"],
  n_heteromodal = group_summary$n[group_summary$mode_group == "Heteromodal"],
  mean_unimodal = group_summary$M[group_summary$mode_group == "Unimodal"],
  sd_unimodal = group_summary$SD[group_summary$mode_group == "Unimodal"],
  n_unimodal = group_summary$n[group_summary$mode_group == "Unimodal"],
  difference_heteromodal_minus_unimodal =
    group_summary$M[group_summary$mode_group == "Heteromodal"] -
    group_summary$M[group_summary$mode_group == "Unimodal"],
  t = unname(tt$statistic),
  df = unname(tt$parameter),
  p = tt$p.value,
  ci_low = tt$conf.int[1],
  ci_high = tt$conf.int[2],
  alternative = tt$alternative,
  method = tt$method
)

write_csv(
  ttest_summary,
  file.path(dout, "PFN_PNC_hetero_vs_uni_ttest.csv")
)

print(group_summary)
print(ttest_summary)
```


### Bar plot of scaling:
```{r}
p_vec_adj<- log_log_wald_bonf[,3]
print(p_vec_adj)
keep_p <- ifelse(p_vec_adj<.05,1,0)
print(keep_p)

betas_from_zero <- log_log_wald_bonf[,2] - 1
sorted_beta = rank(betas_from_zero);
pfn_inAscend_indx <- c()
for (t in c(1:17)) { pfn_inAscend_indx <- append(pfn_inAscend_indx,which(sorted_beta == t))} #if using numbers, switch all pfn_inAscend to pfn_inAscend_indx and comment out next line
pfn_inAscend <- PFN_names[pfn_inAscend_indx]

diff_sig <- read.csv("../../Results/PNC_delta_models/PNC_Group_vs_PFN_boot_results.csv")
diff_sig_p <- diff_sig$p_delta_beta_bonf
stars <- ifelse(diff_sig_p < 0.05, "*", "")

# Using 7 colors scheme for bar plot
data <- data.frame(EffectSizes = as.numeric(betas_from_zero)) 
data$EffectRank <- as.numeric(sorted_beta)
# BorderColor1 is for colors of 1-17 network numbers(to lable the network numbers in a 1-17 order)
BorderColor1 <- c("#E76178", "#7499C2", "#F5BA2E", "#7499C2", "#00A131",
                 "#AF33AD", "#E443FF", "#E76178", "#E443FF", "#AF33AD",
                 "#7499C2", "#E76178", "#7499C2", "#00A131", "#F5BA2E", 
                 "#4E31A8", "#F5BA2E");
				 
# BorderColor2 is for colors of bar fill 1-17 networks (in a 1-17 order). If the bar is nofill, change the code to "#FFFFFF" for that PFN. ("black" is filled with black)
BorderColor2 <- c("#E76178", "#7499C2", "#FFFFFF", "#FFFFFF", "#FFFFFF",
                 "#FFFFFF", "#FFFFFF", "#E76178", "#E443FF", "#FFFFFF",
                 "#FFFFFF", "#FFFFFF", "#FFFFFF", "#00A131", "#F5BA2E", 
                 "#FFFFFF", "#F5BA2E");

# TextColor is for x-axis network label color
TextColor <- c("black", "black", "#767676", "#767676", "#767676",
                 "#767676", "#767676", "black", "black", "#767676",
                 "#767676", "#767676", "#767676", "black", "black", 
                 "#767676", "black");

# Change the color order
BorderColor <- BorderColor1[pfn_inAscend_indx]
BorderColor3 <- BorderColor2[pfn_inAscend_indx]
TextColor_ordered <- TextColor[pfn_inAscend_indx]
stars_ordered <- stars[pfn_inAscend_indx]

#Add stars to data
data$stars <- stars_ordered[sorted_beta]
offset <- 0.02
data$star_y <- ifelse(data$EffectSizes >= 0,
                      data$EffectSizes + offset,
                      data$EffectSizes - offset)
data$star_vjust <- ifelse(data$EffectSizes >= 0, 0, 1)

Fig <- ggplot(data, aes(EffectRank, EffectSizes)) +
  geom_bar(stat = "identity", fill=BorderColor3[sorted_beta], 
           colour = BorderColor[sorted_beta], linetype = "solid", width = 0.8) + 
  geom_text(data = subset(data, stars != ""),
          aes(x = EffectRank, y = star_y, label = stars, vjust = 0.75),
          size = 8,
          fontface = "bold") +
  labs(title = NULL, x = NULL, y = paste0("PFN Allometry (β)")) + theme_classic() +
  theme(plot.title = ggtext::element_markdown(size=25, hjust = 0.5)) +
  theme(axis.text.x = ggtext::element_markdown(size= 22, color = TextColor_ordered), 
        axis.text.y = ggtext::element_markdown(size= 25, color = "black"), 
        axis.title=ggtext::element_markdown(size = 25)) +
  theme(axis.text.x = ggtext::element_markdown(angle = 65, hjust = 1, vjust = 0.5, margin = margin(t=-40)), #if numbers, change to 45 + hjust = 1
    plot.margin = margin(t = 5.5, r = 5.5, b = 40, l = 5.5)) + # comment out if using numbers
  scale_x_discrete(labels = as.character(pfn_inAscend),limits = as.character(sorted_beta)) + #change to pfn_inAscend_indx if using numbers
  scale_y_continuous(
    breaks = c(0.8, 0.9, 1.0, 1.1, 1.2, 1.3) - 1, #set breaks relative to 0
    limits = c(0.8, 1.31) - 1, # match PFN results (more extreme betas)
    labels = c(0.8, 0.9, 1.0, 1.1, 1.2, 1.3)  # set labels so betas are shown relative to 1
  )
Fig
ggsave(paste0("../../Results/PNC_PFN_Age/PNC_PFNs_log_log_scaling_plot_starred_REML_netnames_gray.png"), width = 19, height = 16, dpi = 600, units = "cm");
ggsave(paste0("../../Results/PNC_PFN_Age/PNC_PFNs_log_log_scaling_plot_starred_REML_netnames_gray.pdf"), device = cairo_pdf, width = 19, height = 16, dpi = 600, units = "cm");
```

## log-log models, no euler
```{r}
dout <- "../../Results/PNC_PFN_Age/No_Euler"
dir.create(dout)

summary(gam(log(PFN1_soft_parcel_normed)~log(TC_area)+sex+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML"))
PFN1_gam_no_euler<-gam(log(PFN1_soft_parcel_normed)~log(TC_area)+sex+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML")
#tab_model(PFN1_gam_no_euler,pred.labels = c("Intercept","log TC Area","Sex","Median FD","Age Spline"),dv.labels=c("log PFN1"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = paste(dout,"/PNC_PFNs_PFN1_area_TC_area_no_euler_REML.doc", sep = ""))

summary(gam(log(PFN2_soft_parcel_normed)~log(TC_area)+sex+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML"))
PFN2_gam_no_euler<-gam(log(PFN2_soft_parcel_normed)~log(TC_area)+sex+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML")
#tab_model(PFN2_gam_no_euler,pred.labels = c("Intercept","log TC Area","Sex","Median FD","Age Spline"),dv.labels=c("log PFN2"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = paste(dout,"/PNC_PFNs_PFN2_area_TC_area_no_euler_REML.doc", sep = ""))

summary(gam(log(PFN3_soft_parcel_normed)~log(TC_area)+sex+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML"))
PFN3_gam_no_euler<-gam(log(PFN3_soft_parcel_normed)~log(TC_area)+sex+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML")
#tab_model(PFN3_gam_no_euler,pred.labels = c("Intercept","log TC Area","Sex","Median FD","Age Spline"),dv.labels=c("log PFN3"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = paste(dout,"/PNC_PFNs_PFN3_area_TC_area_no_euler_REML.doc", sep = ""))

summary(gam(log(PFN4_soft_parcel_normed)~log(TC_area)+sex+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML"))
PFN4_gam_no_euler<-gam(log(PFN4_soft_parcel_normed)~log(TC_area)+sex+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML")
#tab_model(PFN4_gam_no_euler,pred.labels = c("Intercept","log TC Area","Sex","Median FD","Age Spline"),dv.labels=c("log PFN4"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = paste(dout,"/PNC_PFNs_PFN4_area_TC_area_no_euler_REML.doc", sep = ""))

summary(gam(log(PFN5_soft_parcel_normed)~log(TC_area)+sex+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML"))
PFN5_gam_no_euler<-gam(log(PFN5_soft_parcel_normed)~log(TC_area)+sex+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML")
#tab_model(PFN5_gam_no_euler,pred.labels = c("Intercept","log TC Area","Sex","Median FD","Age Spline"),dv.labels=c("log PFN5"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = paste(dout,"/PNC_PFNs_PFN5_area_TC_area_no_euler_REML.doc", sep = ""))

summary(gam(log(PFN6_soft_parcel_normed)~log(TC_area)+sex+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML"))
PFN6_gam_no_euler<-gam(log(PFN6_soft_parcel_normed)~log(TC_area)+sex+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML")
#tab_model(PFN6_gam_no_euler,pred.labels = c("Intercept","log TC Area","Sex","Median FD","Age Spline"),dv.labels=c("log PFN6"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = paste(dout,"/PNC_PFNs_PFN6_area_TC_area_no_euler_REML.doc", sep = ""))

summary(gam(log(PFN7_soft_parcel_normed)~log(TC_area)+sex+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML"))
PFN7_gam_no_euler<-gam(log(PFN7_soft_parcel_normed)~log(TC_area)+sex+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML")
#tab_model(PFN7_gam_no_euler,pred.labels = c("Intercept","log TC Area","Sex","Median FD","Age Spline"),dv.labels=c("log PFN7"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = paste(dout,"/PNC_PFNs_PFN7_area_TC_area_no_euler_REML.doc", sep = ""))

summary(gam(log(PFN8_soft_parcel_normed)~log(TC_area)+sex+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML"))
PFN8_gam_no_euler<-gam(log(PFN8_soft_parcel_normed)~log(TC_area)+sex+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML")
#tab_model(PFN8_gam_no_euler,pred.labels = c("Intercept","log TC Area","Sex","Median FD","Age Spline"),dv.labels=c("log PFN8"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = paste(dout,"/PNC_PFNs_PFN8_area_TC_area_no_euler_REML.doc", sep = ""))

summary(gam(log(PFN9_soft_parcel_normed)~log(TC_area)+sex+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML"))
PFN9_gam_no_euler<-gam(log(PFN9_soft_parcel_normed)~log(TC_area)+sex+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML")
#tab_model(PFN9_gam_no_euler,pred.labels = c("Intercept","log TC Area","Sex","Median FD","Age Spline"),dv.labels=c("log PFN9"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = paste(dout,"/PNC_PFNs_PFN9_area_TC_area_no_euler_REML.doc", sep = ""))

summary(gam(log(PFN10_soft_parcel_normed)~log(TC_area)+sex+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML"))
PFN10_gam_no_euler<-gam(log(PFN10_soft_parcel_normed)~log(TC_area)+sex+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML")
#tab_model(PFN10_gam_no_euler,pred.labels = c("Intercept","log TC Area","Sex","Median FD","Age Spline"),dv.labels=c("log PFN10"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = paste(dout,"/PNC_PFNs_PFN10_area_TC_area_no_euler_REML.doc", sep = ""))

summary(gam(log(PFN11_soft_parcel_normed)~log(TC_area)+sex+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML"))
PFN11_gam_no_euler<-gam(log(PFN11_soft_parcel_normed)~log(TC_area)+sex+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML")
#tab_model(PFN11_gam_no_euler,pred.labels = c("Intercept","log TC Area","Sex","Median FD","Age Spline"),dv.labels=c("log PFN11"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = paste(dout,"/PNC_PFNs_PFN11_area_TC_area_no_euler_REML.doc", sep = ""))

summary(gam(log(PFN12_soft_parcel_normed)~log(TC_area)+sex+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML"))
PFN12_gam_no_euler<-gam(log(PFN12_soft_parcel_normed)~log(TC_area)+sex+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML")
#tab_model(PFN12_gam_no_euler,pred.labels = c("Intercept","log TC Area","Sex","Median FD","Age Spline"),dv.labels=c("log PFN12"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = paste(dout,"/PNC_PFNs_PFN12_area_TC_area_no_euler_REML.doc", sep = ""))

summary(gam(log(PFN13_soft_parcel_normed)~log(TC_area)+sex+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML"))
PFN13_gam_no_euler<-gam(log(PFN13_soft_parcel_normed)~log(TC_area)+sex+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML")
#tab_model(PFN13_gam_no_euler,pred.labels = c("Intercept","log TC Area","Sex","Median FD","Age Spline"),dv.labels=c("log PFN13"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = paste(dout,"/PNC_PFNs_PFN13_area_TC_area_no_euler_REML.doc", sep = ""))

summary(gam(log(PFN14_soft_parcel_normed)~log(TC_area)+sex+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML"))
PFN14_gam_no_euler<-gam(log(PFN14_soft_parcel_normed)~log(TC_area)+sex+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML")
#tab_model(PFN14_gam_no_euler,pred.labels = c("Intercept","log TC Area","Sex","Median FD","Age Spline"),dv.labels=c("log PFN14"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = paste(dout,"/PNC_PFNs_PFN14_area_TC_area_no_euler_REML.doc", sep = ""))

summary(gam(log(PFN15_soft_parcel_normed)~log(TC_area)+sex+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML"))
PFN15_gam_no_euler<-gam(log(PFN15_soft_parcel_normed)~log(TC_area)+sex+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML")
#tab_model(PFN15_gam_no_euler,pred.labels = c("Intercept","log TC Area","Sex","Median FD","Age Spline"),dv.labels=c("log PFN15"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = paste(dout,"/PNC_PFNs_PFN15_area_TC_area_no_euler_REML.doc", sep = ""))

summary(gam(log(PFN16_soft_parcel_normed)~log(TC_area)+sex+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML"))
PFN16_gam_no_euler<-gam(log(PFN16_soft_parcel_normed)~log(TC_area)+sex+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML")
#tab_model(PFN16_gam_no_euler,pred.labels = c("Intercept","log TC Area","Sex","Median FD","Age Spline"),dv.labels=c("log PFN16"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = paste(dout,"/PNC_PFNs_PFN16_area_TC_area_no_euler_REML.doc", sep = ""))

summary(gam(log(PFN17_soft_parcel_normed)~log(TC_area)+sex+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML"))
PFN17_gam_no_euler<-gam(log(PFN17_soft_parcel_normed)~log(TC_area)+sex+median_fd_combined+s(age,k=4),data=PNC_all,method = "REML")
#tab_model(PFN17_gam_no_euler,pred.labels = c("Intercept","log TC Area","Sex","Median FD","Age Spline"),dv.labels=c("log PFN17"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = paste(dout,"/PNC_PFNs_PFN17_area_TC_area_no_euler_REML.doc", sep = ""))

```

# Get significance of beta scaling term via Wald test in no euler models
```{r}
dout <- "../../Results/PNC_PFN_Age/No_Euler"

log_log_results_no_euler <- matrix(0,17,2)

for (net in c(1:17)) {
  beta <- summary(get(paste0("PFN",net,"_gam_no_euler")))$p.table["log(TC_area)", "Estimate"]
  SE <- summary(get(paste0("PFN",net,"_gam_no_euler")))$p.table["log(TC_area)", "Std. Error"]
  z_val <- (beta - 1) / SE # Null is beta = 1 (isometry, linear scaling)
  #df <- df.residual(get(paste0("PFN",net,"_gam_no_euler")))
  log_log_results_no_euler[net,1] <- beta
  log_log_results_no_euler[net,2] <- 2 * (1 - pnorm(abs(z_val))) #Wald test
}

pvals_bonf <- p.adjust(log_log_results_no_euler[,2], method = "bonf")
#PFN_names <- c("PFN1", "PFN2", "PFN3", "PFN4", "PFN5", "PFN6", "PFN7", "PFN8", "PFN9", "PFN10", "PFN11", "PFN12", "PFN13", "PFN14", "PFN15", "PFN16", "PFN17")
log_log_wald_no_euler_bonf <-  data.frame(PFN = PFN_names, beta = log_log_results_no_euler[,1], pvals_bonf = pvals_bonf)

#write_csv(log_log_wald_no_euler_bonf,paste0(dout,"/PNC_PFNs_log_log_summary_results_bonf_no_euler_REML_netnames.csv"))
```

### Bar plot of scaling for no euler models:
```{r}
p_vec_adj<- log_log_wald_no_euler_bonf[,3]
print(p_vec_adj)
keep_p <- ifelse(p_vec_adj<.05,1,0)
print(keep_p)

betas_from_zero <- log_log_wald_no_euler_bonf[,2] - 1
sorted_beta = rank(betas_from_zero);
pfn_inAscend_indx <- c()
for (t in c(1:17)) { pfn_inAscend_indx <- append(pfn_inAscend_indx,which(sorted_beta == t))} #if using numbers, switch all pfn_inAscend to pfn_inAscend_indx and comment out next line
pfn_inAscend <- PFN_names[pfn_inAscend_indx]

# Using 7 colors scheme for bar plot
data <- data.frame(EffectSizes = as.numeric(betas_from_zero)) 
data$EffectRank <- as.numeric(sorted_beta)
# BorderColor1 is for colors of 1-17 network numbers(to lable the network numbers in a 1-17 order)
BorderColor1 <- c("#E76178", "#7499C2", "#F5BA2E", "#7499C2", "#00A131",
                 "#AF33AD", "#E443FF", "#E76178", "#E443FF", "#AF33AD",
                 "#7499C2", "#E76178", "#7499C2", "#00A131", "#F5BA2E", 
                 "#4E31A8", "#F5BA2E");
				 
# BorderColor2 is for colors of bar fill 1-17 networks (in a 1-17 order). If the bar is nofill, change the code to "#FFFFFF" for that PFN. ("black" is filled with black)
BorderColor2 <- c("#E76178", "#7499C2", "#FFFFFF", "#FFFFFF", "#FFFFFF",
                 "#FFFFFF", "#FFFFFF", "#E76178", "#E443FF", "#FFFFFF",
                 "#FFFFFF", "#FFFFFF", "#FFFFFF", "#00A131", "#F5BA2E", 
                 "#FFFFFF", "#F5BA2E");

# TextColor is for x-axis network label color
TextColor <- c("black", "black", "#767676", "#767676", "#767676",
                 "#767676", "#767676", "black", "black", "#767676",
                 "#767676", "#767676", "#767676", "black", "black", 
                 "#767676", "black");

# Change the color order
BorderColor <- BorderColor1[pfn_inAscend_indx]
BorderColor3 <- BorderColor2[pfn_inAscend_indx]
TextColor_ordered <- TextColor[pfn_inAscend_indx]

Fig <- ggplot(data, aes(EffectRank, EffectSizes)) +
  geom_bar(stat = "identity", fill=BorderColor3[sorted_beta], 
           colour = BorderColor[sorted_beta], linetype = "solid", width = 0.8) + 
  labs(title = NULL, x = NULL, y = paste0("PFN Allometry (β)")) + theme_classic() +
  theme(plot.title = ggtext::element_markdown(size=25, hjust = 0.5)) +
  theme(axis.text.x = ggtext::element_markdown(size= 22, color = TextColor_ordered), 
        axis.text.y = ggtext::element_markdown(size= 25, color = "black"), 
        axis.title=ggtext::element_markdown(size = 25)) +
  theme(axis.text.x = ggtext::element_markdown(angle = 65, hjust = 1, vjust = 0.5, margin = margin(t=-40)), #if numbers, change to 45 + hjust = 1
    plot.margin = margin(t = 5.5, r = 5.5, b = 40, l = 5.5)) + # comment out if using numbers
  scale_x_discrete(labels = as.character(pfn_inAscend),limits = as.character(sorted_beta)) + #change to pfn_inAscend_indx if using numbers
  scale_y_continuous(
    breaks = c(0.8, 0.9, 1.0, 1.1, 1.2, 1.3) - 1, #set breaks relative to 0
    limits = c(0.8, 1.31) - 1, # match PFN results (more extreme betas)
    labels = c(0.8, 0.9, 1.0, 1.1, 1.2, 1.3)  # set labels so betas are shown relative to 1
  )
Fig
ggsave(paste0("../../Results/PNC_PFN_Age/No_Euler/PNC_PFNs_log_log_scaling_plot_bonf_no_euler_REML_netnames_gray.png"), width = 19, height = 16, dpi = 600, units = "cm");
ggsave(paste0("../../Results/PNC_PFN_Age/No_Euler/PNC_PFNs_log_log_scaling_plot_bonf_no_euler_REML_netnames_gray.pdf"), device = cairo_pdf, width = 19, height = 16, dpi = 600, units = "cm");
```

## log-log models no age spline
```{r}
dout <- "../../Results/PNC_PFN_No_age"
dir.create(dout)

summary(gam(log(PFN1_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined,data=PNC_all,method = "REML"))
PFN1_gam_no_age<-gam(log(PFN1_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined,data=PNC_all,method = "REML")
#tab_model(PFN1_gam_no_age,pred.labels = c("Intercept","log TC Area","Sex","Euler Number","Median FD"),dv.labels=c("log PFN1"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = paste(dout,"/PNC_PFNs_PFN1_area_TC_area_REML.doc", sep = ""))

summary(gam(log(PFN2_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined,data=PNC_all,method = "REML"))
PFN2_gam_no_age<-gam(log(PFN2_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined,data=PNC_all,method = "REML")
#tab_model(PFN2_gam_no_age,pred.labels = c("Intercept","log TC Area","Sex","Euler Number","Median FD"),dv.labels=c("log PFN2"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = paste(dout,"/PNC_PFNs_PFN2_area_TC_area_REML.doc", sep = ""))

summary(gam(log(PFN3_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined,data=PNC_all,method = "REML"))
PFN3_gam_no_age<-gam(log(PFN3_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined,data=PNC_all,method = "REML")
#tab_model(PFN3_gam_no_age,pred.labels = c("Intercept","log TC Area","Sex","Euler Number","Median FD"),dv.labels=c("log PFN3"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = paste(dout,"/PNC_PFNs_PFN3_area_TC_area_REML.doc", sep = ""))

summary(gam(log(PFN4_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined,data=PNC_all,method = "REML"))
PFN4_gam_no_age<-gam(log(PFN4_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined,data=PNC_all,method = "REML")
#tab_model(PFN4_gam_no_age,pred.labels = c("Intercept","log TC Area","Sex","Euler Number","Median FD"),dv.labels=c("log PFN4"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = paste(dout,"/PNC_PFNs_PFN4_area_TC_area_REML.doc", sep = ""))

summary(gam(log(PFN5_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined,data=PNC_all,method = "REML"))
PFN5_gam_no_age<-gam(log(PFN5_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined,data=PNC_all,method = "REML")
#tab_model(PFN5_gam_no_age,pred.labels = c("Intercept","log TC Area","Sex","Euler Number","Median FD"),dv.labels=c("log PFN5"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = paste(dout,"/PNC_PFNs_PFN5_area_TC_area_REML.doc", sep = ""))

summary(gam(log(PFN6_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined,data=PNC_all,method = "REML"))
PFN6_gam_no_age<-gam(log(PFN6_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined,data=PNC_all,method = "REML")
#tab_model(PFN6_gam_no_age,pred.labels = c("Intercept","log TC Area","Sex","Euler Number","Median FD"),dv.labels=c("log PFN6"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = paste(dout,"/PNC_PFNs_PFN6_area_TC_area_REML.doc", sep = ""))

summary(gam(log(PFN7_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined,data=PNC_all,method = "REML"))
PFN7_gam_no_age<-gam(log(PFN7_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined,data=PNC_all,method = "REML")
#tab_model(PFN7_gam_no_age,pred.labels = c("Intercept","log TC Area","Sex","Euler Number","Median FD"),dv.labels=c("log PFN7"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = paste(dout,"/PNC_PFNs_PFN7_area_TC_area_REML.doc", sep = ""))

summary(gam(log(PFN8_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined,data=PNC_all,method = "REML"))
PFN8_gam_no_age<-gam(log(PFN8_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined,data=PNC_all,method = "REML")
#tab_model(PFN8_gam_no_age,pred.labels = c("Intercept","log TC Area","Sex","Euler Number","Median FD"),dv.labels=c("log PFN8"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = paste(dout,"/PNC_PFNs_PFN8_area_TC_area_REML.doc", sep = ""))

summary(gam(log(PFN9_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined,data=PNC_all,method = "REML"))
PFN9_gam_no_age<-gam(log(PFN9_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined,data=PNC_all,method = "REML")
#tab_model(PFN9_gam_no_age,pred.labels = c("Intercept","log TC Area","Sex","Euler Number","Median FD"),dv.labels=c("log PFN9"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = paste(dout,"/PNC_PFNs_PFN9_area_TC_area_REML.doc", sep = ""))

summary(gam(log(PFN10_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined,data=PNC_all,method = "REML"))
PFN10_gam_no_age<-gam(log(PFN10_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined,data=PNC_all,method = "REML")
#tab_model(PFN10_gam_no_age,pred.labels = c("Intercept","log TC Area","Sex","Euler Number","Median FD"),dv.labels=c("log PFN10"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = paste(dout,"/PNC_PFNs_PFN10_area_TC_area_REML.doc", sep = ""))

summary(gam(log(PFN11_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined,data=PNC_all,method = "REML"))
PFN11_gam_no_age<-gam(log(PFN11_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined,data=PNC_all,method = "REML")
#tab_model(PFN11_gam_no_age,pred.labels = c("Intercept","log TC Area","Sex","Euler Number","Median FD"),dv.labels=c("log PFN11"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = paste(dout,"/PNC_PFNs_PFN11_area_TC_area_REML.doc", sep = ""))

summary(gam(log(PFN12_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined,data=PNC_all,method = "REML"))
PFN12_gam_no_age<-gam(log(PFN12_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined,data=PNC_all,method = "REML")
#tab_model(PFN12_gam_no_age,pred.labels = c("Intercept","log TC Area","Sex","Euler Number","Median FD"),dv.labels=c("log PFN12"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = paste(dout,"/PNC_PFNs_PFN12_area_TC_area_REML.doc", sep = ""))

summary(gam(log(PFN13_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined,data=PNC_all,method = "REML"))
PFN13_gam_no_age<-gam(log(PFN13_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined,data=PNC_all,method = "REML")
#tab_model(PFN13_gam_no_age,pred.labels = c("Intercept","log TC Area","Sex","Euler Number","Median FD"),dv.labels=c("log PFN13"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = paste(dout,"/PNC_PFNs_PFN13_area_TC_area_REML.doc", sep = ""))

summary(gam(log(PFN14_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined,data=PNC_all,method = "REML"))
PFN14_gam_no_age<-gam(log(PFN14_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined,data=PNC_all,method = "REML")
#tab_model(PFN14_gam_no_age,pred.labels = c("Intercept","log TC Area","Sex","Euler Number","Median FD"),dv.labels=c("log PFN14"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = paste(dout,"/PNC_PFNs_PFN14_area_TC_area_REML.doc", sep = ""))

summary(gam(log(PFN15_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined,data=PNC_all,method = "REML"))
PFN15_gam_no_age<-gam(log(PFN15_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined,data=PNC_all,method = "REML")
#tab_model(PFN15_gam_no_age,pred.labels = c("Intercept","log TC Area","Sex","Euler Number","Median FD"),dv.labels=c("log PFN15"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = paste(dout,"/PNC_PFNs_PFN15_area_TC_area_REML.doc", sep = ""))

summary(gam(log(PFN16_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined,data=PNC_all,method = "REML"))
PFN16_gam_no_age<-gam(log(PFN16_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined,data=PNC_all,method = "REML")
#tab_model(PFN16_gam_no_age,pred.labels = c("Intercept","log TC Area","Sex","Euler Number","Median FD"),dv.labels=c("log PFN16"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = paste(dout,"/PNC_PFNs_PFN16_area_TC_area_REML.doc", sep = ""))

summary(gam(log(PFN17_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined,data=PNC_all,method = "REML"))
PFN17_gam_no_age<-gam(log(PFN17_soft_parcel_normed)~log(TC_area)+sex+euler+median_fd_combined,data=PNC_all,method = "REML")
#tab_model(PFN17_gam_no_age,pred.labels = c("Intercept","log TC Area","Sex","Euler Number","Median FD"),dv.labels=c("log PFN17"),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = paste(dout,"/PNC_PFNs_PFN17_area_TC_area_REML.doc", sep = ""))

```

# Get significance of beta scaling term via Wald test in no age spline models
```{r}
dout <- "../../Results/PNC_PFN_No_age"

log_log_results_no_age_cov <- matrix(0,17,2)

for (net in c(1:17)) {
  beta <- summary(get(paste0("PFN",net,"_gam_no_age")))$p.table["log(TC_area)", "Estimate"]
  SE <- summary(get(paste0("PFN",net,"_gam_no_age")))$p.table["log(TC_area)", "Std. Error"]
  z_val <- (beta - 1) / SE # Null is beta = 1 (isometry, linear scaling)
  #df <- df.residual(get(paste0("PFN",net,"_gam_no_age")))
  log_log_results_no_age_cov[net,1] <- beta
  log_log_results_no_age_cov[net,2] <- 2 * (1 - pnorm(abs(z_val))) #Wald test
}

pvals_bonf <- p.adjust(log_log_results_no_age_cov[,2], method = "bonf")
#PFN_names <- c("PFN1", "PFN2", "PFN3", "PFN4", "PFN5", "PFN6", "PFN7", "PFN8", "PFN9", "PFN10", "PFN11", "PFN12", "PFN13", "PFN14", "PFN15", "PFN16", "PFN17")
log_log_wald_no_age_cov_bonf <-  data.frame(PFN = PFN_names, beta = log_log_results_no_age_cov[,1], pvals_bonf = pvals_bonf)

#write_csv(log_log_wald_no_age_cov_bonf,paste0(dout,"/PNC_PFNs_log_log_no_age_summary_results_bonf_REML_netnames.csv"))
```

### Bar plot of scaling (no age term):
```{r}
p_vec_adj<- log_log_wald_no_age_cov_bonf[,3]
print(p_vec_adj)
keep_p <- ifelse(p_vec_adj<.05,1,0)
print(keep_p)

betas_from_zero <- log_log_wald_no_age_cov_bonf[,2] - 1
sorted_beta = rank(betas_from_zero);
pfn_inAscend_indx <- c()
for (t in c(1:17)) { pfn_inAscend_indx <- append(pfn_inAscend_indx,which(sorted_beta == t))} #if using numbers, switch all pfn_inAscend to pfn_inAscend_indx and comment out next line
pfn_inAscend <- PFN_names[pfn_inAscend_indx]

# Using 7 colors scheme for bar plot
data <- data.frame(EffectSizes = as.numeric(betas_from_zero)) 
data$EffectRank <- as.numeric(sorted_beta)
# BorderColor1 is for colors of 1-17 network numbers(to lable the network numbers in a 1-17 order)
BorderColor1 <- c("#E76178", "#7499C2", "#F5BA2E", "#7499C2", "#00A131",
                 "#AF33AD", "#E443FF", "#E76178", "#E443FF", "#AF33AD",
                 "#7499C2", "#E76178", "#7499C2", "#00A131", "#F5BA2E", 
                 "#4E31A8", "#F5BA2E");
				 
# BorderColor2 is for colors of bar fill 1-17 networks (in a 1-17 order). If the bar is nofill, change the code to "#FFFFFF" for that PFN. ("black" is filled with black)
BorderColor2 <- c("#E76178", "#7499C2", "#FFFFFF", "#FFFFFF", "#FFFFFF",
                 "#FFFFFF", "#FFFFFF", "#E76178", "#E443FF", "#FFFFFF",
                 "#FFFFFF", "#FFFFFF", "#FFFFFF", "#00A131", "#F5BA2E", 
                 "#FFFFFF", "#F5BA2E");

# TextColor is for x-axis network label color
TextColor <- c("black", "black", "#767676", "#767676", "#767676",
                 "#767676", "#767676", "black", "black", "#767676",
                 "#767676", "#767676", "#767676", "black", "black", 
                 "#767676", "black");

# Change the color order
BorderColor <- BorderColor1[pfn_inAscend_indx]
BorderColor3 <- BorderColor2[pfn_inAscend_indx]
TextColor_ordered <- TextColor[pfn_inAscend_indx]

Fig <- ggplot(data, aes(EffectRank, EffectSizes)) +
  geom_bar(stat = "identity", fill=BorderColor3[sorted_beta], 
           colour = BorderColor[sorted_beta], linetype = "solid", width = 0.8) + 
  labs(title = NULL, x = NULL, y = paste0("PFN Allometry (β)")) + theme_classic() +
  theme(plot.title = ggtext::element_markdown(size=25, hjust = 0.5)) +
  theme(axis.text.x = ggtext::element_markdown(size= 22, color = TextColor_ordered), 
        axis.text.y = ggtext::element_markdown(size= 25, color = "black"), 
        axis.title=ggtext::element_markdown(size = 25)) +
  theme(axis.text.x = ggtext::element_markdown(angle = 65, hjust = 1, vjust = 0.5, margin = margin(t=-40)), #if numbers, change to 45 + hjust = 1
    plot.margin = margin(t = 5.5, r = 5.5, b = 40, l = 5.5)) + # comment out if using numbers
  scale_x_discrete(labels = as.character(pfn_inAscend),limits = as.character(sorted_beta)) + #change to pfn_inAscend_indx if using numbers
  scale_y_continuous(
    breaks = c(0.8, 0.9, 1.0, 1.1, 1.2, 1.3) - 1, #set breaks relative to 0
    limits = c(0.8, 1.31) - 1, # match PFN results (more extreme betas)
    labels = c(0.8, 0.9, 1.0, 1.1, 1.2, 1.3)  # set labels so betas are shown relative to 1
  )
Fig
ggsave(paste0("../../Results/PNC_PFN_No_age/PNC_PFNs_log_log_scaling_no_age_plot_bonf_REML_netnames_gray.png"), width = 19, height = 16, dpi = 600, units = "cm");
ggsave(paste0("../../Results/PNC_PFN_No_age/PNC_PFNs_log_log_scaling_no_age_plot_bonf_REML_netnames_gray.pdf"), device = cairo_pdf, width = 19, height = 16, dpi = 600, units = "cm")
```
