
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
library(readr)
library(sjPlot)
library(mgcv)
library(boot)
library(boot.pval)
library(parallel)
```

#Import areas and demographics
```{r}
PNC_TC_and_group_network_areas <- read.csv("../../Inputs/PNC_summary_group.csv") # n = 1598
colnames(PNC_TC_and_group_network_areas)[1] <- "participant_id"

PNC_TC_and_PFNs_network_areas <- read.csv("../../Inputs/PNC_summary_PFNs.csv") # n = 1482
colnames(PNC_TC_and_PFNs_network_areas)[1] <- "participant_id"
colnames(PNC_TC_and_PFNs_network_areas)[3] <- "PFN1_soft_parcel_normed"
colnames(PNC_TC_and_PFNs_network_areas)[4] <- "PFN2_soft_parcel_normed"
colnames(PNC_TC_and_PFNs_network_areas)[5] <- "PFN3_soft_parcel_normed"
colnames(PNC_TC_and_PFNs_network_areas)[6] <- "PFN4_soft_parcel_normed"
colnames(PNC_TC_and_PFNs_network_areas)[7] <- "PFN5_soft_parcel_normed"
colnames(PNC_TC_and_PFNs_network_areas)[8] <- "PFN6_soft_parcel_normed"
colnames(PNC_TC_and_PFNs_network_areas)[9] <- "PFN7_soft_parcel_normed"
colnames(PNC_TC_and_PFNs_network_areas)[10] <- "PFN8_soft_parcel_normed"
colnames(PNC_TC_and_PFNs_network_areas)[11] <- "PFN9_soft_parcel_normed"

PNC_demos <- read.csv("../../Inputs/filtered_demo_PNC.csv") #n = 1332

PNC_Group <- merge(PNC_TC_and_group_network_areas,PNC_demos,by="participant_id") # n = 1332
PNC_PFNs <- merge(PNC_TC_and_PFNs_network_areas,PNC_demos,by="participant_id") # n = 1332

#Check equivalence of TC areas
TC_area_equivalence <- identical(PNC_Group$TC_area, PNC_PFNs$TC_area)

```

#Merge together Group and PFN area data for PNC
```{r}
# Confirm participant ordering before combining
stopifnot(
  identical(PNC_Group$participant_id,
            PNC_PFNs$participant_id)
)

# Rename group-atlas columns
PNC_Group_boot <- PNC_Group
names(PNC_Group_boot) <- gsub(
  "PFN",
  "group_PFN",
  names(PNC_Group_boot)
)
names(PNC_Group_boot) <- gsub(
  "_soft_parcel_normed",
  "",
  names(PNC_Group_boot)
)

# Rename PFN columns
PNC_PFNs_boot <- PNC_PFNs
names(PNC_PFNs_boot) <- gsub(
  "_soft_parcel_normed",
  "",
  names(PNC_PFNs_boot)
)

# Append group network areas
group_cols <- paste0("group_PFN", 1:17)

PNC_test_null <- cbind(
  PNC_PFNs_boot,
  PNC_Group_boot[, group_cols, drop = FALSE]
)

pfn_cols <- paste0("PFN", 1:17)
group_cols <- paste0("group_PFN", 1:17)

stopifnot(
  all(pfn_cols %in% names(PNC_PFNs_boot)),
  all(group_cols %in% names(PNC_Group_boot))
)
```

#Bootstrap of delta between betas (difference between betas, 2-tailed + difference in deviation from isometry, 2-tailed)
```{r}
# Randomly sample N participants with replacement from the original N participants.
# Fit the PFN GAM on that resampled dataset.
# Fit the corresponding group-atlas GAM on the exact same resampled participants.
# Extract the two cortical-area scaling coefficients: PFN + Group
# Calculate the two comparison statistics: PFN-Group and |PFN-1| - |Group-1|
# x 5000

set.seed(1)
boot_n <- 5000
nets <- 1:17
make_boot_stat <- function(y_pfn, y_group) {

  function(data, indices) {

    d <- data[indices, , drop = FALSE]

    fit_pfn <- gam(
      log(d[[y_pfn]]) ~
        log(TC_area) +
        sex +
        euler +
        median_fd_combined +
        s(age, k = 4),
      data = d,
      method = "REML"
    )

    fit_group <- gam(
      log(d[[y_group]]) ~
        log(TC_area) +
        sex +
        euler +
        median_fd_combined +
        s(age, k = 4),
      data = d,
      method = "REML"
    )

    beta_pfn <- coef(fit_pfn)[["log(TC_area)"]]
    beta_group <- coef(fit_group)[["log(TC_area)"]]

    c(
      beta_pfn = beta_pfn,
      beta_group = beta_group,
      delta_diff = beta_pfn - beta_group,
      delta_dev =
        abs(beta_pfn - 1) -
        abs(beta_group - 1)
    )
  }
}

# Number of workers
# Leaving 1-2 logical cores free is usually sensible on a local machine
n_cores <- max(1, detectCores() - 2)

# Create Windows PSOCK cluster
cl <- makeCluster(n_cores)

# Load required packages on every worker
clusterEvalQ(cl, {
  library(mgcv)
  library(boot)
})

# Reproducible independent RNG streams for workers
clusterSetRNGStream(cl, iseed = 1)

boot_results <- vector("list", length(nets))
names(boot_results) <- paste0("PFN", nets)

sample_sizes <- integer(length(nets))

for (net in nets) {

  y_pfn <- paste0("PFN", net)
  y_group <- paste0("group_PFN", net)

  required_vars <- c(
    y_pfn,
    y_group,
    "TC_area",
    "sex",
    "euler",
    "median_fd_combined",
    "age"
  )

  d_net <- PNC_test_null[
    complete.cases(
      PNC_test_null[, required_vars]
    ),
    ,
    drop = FALSE
  ]

  # Variables that are logged must be > 0
  d_net <- d_net[
    d_net[[y_pfn]] > 0 &
    d_net[[y_group]] > 0 &
    d_net$TC_area > 0,
    ,
    drop = FALSE
  ]

  sample_sizes[net] <- nrow(d_net)

  boot_results[[y_pfn]] <- boot(
    data = d_net,
    statistic = make_boot_stat(
      y_pfn = y_pfn,
      y_group = y_group
    ),
    R = boot_n,

    # Windows parallelization
    parallel = "snow",
    ncpus = n_cores,
    cl = cl
  )

  message(
    "Finished network ", net,
    " of ", length(nets),
    "; n = ", nrow(d_net)
  )
}

# shut down the workers when finished
stopCluster(cl)
```

#Compare delta of boostrapped PFN and Group Atlas betas of TC_area effect (difference in deviation from isometry, 2-tailed + difference between betas, 2-tailed)
```{r}
dout <- "../../Results/PNC_Delta_models"
dir.create(dout)

# Bias-corrected and accelerated (BCa) bootstrap confidence intervals:
# - bias correction accounts for displacement of the bootstrap distribution relative to the observed estimate
# - acceleration accounts for changes in the standard error with the underlying data, using empirical influence information

# Bootstrap p-values are obtained by inversion of the corresponding BCa confidence-interval procedure.

results <- vector("list", length(nets))

for (net in nets) {

  pfn_name <- paste0("PFN", net)
  b <- boot_results[[pfn_name]]

  # observed statistics
  beta_pfn_obs   <- b$t0[1]
  beta_group_obs <- b$t0[2]
  delta_diff_obs <- b$t0[3]
  delta_dev_obs  <- b$t0[4]

  
  n_boot_valid <- sum(
    apply(b$t, 1, function(x) all(is.finite(x)))
  )
  
  prop_boot_valid <- n_boot_valid / boot_n
  
  # BCa confidence intervals
  ci_diff <- boot.ci(
    b,
    type = "bca",
    index = 3
  )$bca[4:5]

  ci_dev <- boot.ci(
    b,
    type = "bca",
    index = 4
  )$bca[4:5]
  
  # Bootstrap CIs of betas
  ci_beta_pfn <- boot.ci(
    b,
    type = "bca",
    index = 1
  )$bca[4:5]
  
  ci_beta_group <- boot.ci(
    b,
    type = "bca",
    index = 2
  )$bca[4:5]
  
  # Bootstrap p-values from CI inversion
  p_diff <- boot.pval(
    b,
    type = "bca",
    theta_null = 0,
    alternative = "two.sided",
    index = 3
  )

  p_dev <- boot.pval(
    b,
    type = "bca",
    theta_null = 0,
    alternative = "two.sided", #or "greater" for one-sided
    index = 4
  )

  results[[net]] <- data.frame(
    PFN = pfn_name,
    
    n_boot_valid = n_boot_valid,
    prop_boot_valid = prop_boot_valid,
  
    beta_pfn = beta_pfn_obs,
    beta_pfn_CI_low = ci_beta_pfn[1],
    beta_pfn_CI_high = ci_beta_pfn[2],
  
    beta_group = beta_group_obs,
    beta_group_CI_low = ci_beta_group[1],
    beta_group_CI_high = ci_beta_group[2],
  
    delta_beta = delta_diff_obs,
    delta_beta_CI_low = ci_diff[1],
    delta_beta_CI_high = ci_diff[2],
    p_delta_beta = p_diff,
  
    delta_deviation = delta_dev_obs,
    delta_deviation_CI_low = ci_dev[1],
    delta_deviation_CI_high = ci_dev[2],
    p_delta_deviation = p_dev
  )
}

results <- bind_rows(results)

results <- results %>%
  mutate(
    p_delta_beta_bonf =
      p.adjust(
        p_delta_beta,
        method = "bonferroni"
      ),

    p_delta_deviation_bonf =
      p.adjust(
        p_delta_deviation,
        method = "bonferroni"
      )
  )

write_csv(results,paste0(dout,"/PNC_Group_vs_PFN_boot_results_two_sided.csv"))
```

# Higher-order vs lower-order network t-tests on absolute deltas
```{r}

dout <- "../../Results/PNC_Delta_models"

results <- read_csv(
  paste0(dout, "/PNC_Group_vs_PFN_boot_results_two_sided.csv")
)

# Lower-order networks
lower_order_nets <- c(2, 4, 6, 10, 11, 13, 16)

network_order_df <- data.frame(
  PFN = paste0("PFN", 1:17),
  network_order = ifelse(
    1:17 %in% lower_order_nets,
    "lower_order",
    "higher_order"
  )
)

results <- results %>%
  left_join(network_order_df, by = "PFN") %>%
  mutate(
    abs_delta_beta = abs(delta_beta),
    abs_delta_deviation = abs(delta_deviation)
  )

# Welch two-sample t-tests; does not assume equal variance
ttest_abs_delta_beta <- t.test(
  abs_delta_beta ~ network_order,
  data = results,
  var.equal = FALSE
)

# Compact summary table
network_order_ttest_results <- bind_rows(
  data.frame(
    outcome = "abs_delta_beta",
    mean_higher_order = mean(results$abs_delta_beta[results$network_order == "higher_order"], na.rm = TRUE),
    mean_lower_order = mean(results$abs_delta_beta[results$network_order == "lower_order"], na.rm = TRUE),
    difference_higher_minus_lower =
      mean(results$abs_delta_beta[results$network_order == "higher_order"], na.rm = TRUE) -
      mean(results$abs_delta_beta[results$network_order == "lower_order"], na.rm = TRUE),
    t = unname(ttest_abs_delta_beta$statistic),
    df = unname(ttest_abs_delta_beta$parameter),
    p = ttest_abs_delta_beta$p.value,
    ci_low = ttest_abs_delta_beta$conf.int[1],
    ci_high = ttest_abs_delta_beta$conf.int[2]
  )
)

print(network_order_ttest_results)

write_csv(
  network_order_ttest_results,
  paste0(dout, "/PNC_higher_vs_lower_order_abs_delta_ttests.csv")
)
```