---
title: "Demographic Match PNC to 22q Sample"
output:
  html_document:
    df_print: paged
---

```{r}
library(MatchIt)
library(tidyr)
library(dplyr)
library(cobalt)
library(ggplot2)
library(finalfit)
library(Hmisc)
library(tidyverse)
library(rstatix)
library(ggpubr)
```

#Read in 22q and PNC demographics data
```{r}
demo_PNC <- read_csv('C:/Users/kevin/OneDrive/Documents/NGG_PhD/Alexander-Bloch/22q_Project/Analyses/Inputs/filtered_demo_PNC.csv') # N = 1332
demo_22q <- read_csv('C:/Users/kevin/OneDrive/Documents/NGG_PhD/Alexander-Bloch/22q_Project/Analyses/Inputs/filtered_demo_22q.csv') # N = 100
colnames(demo_PNC)[1] <- "subject"
```

# Initial demographic/QC comparison (median fd, Euler, age, sex, race)
```{r}
col_names <- c("PNC","SD_PNC","22q","SD_22q","p value")
row_names <- c("Median_FD", "Euler", "Age", "Female_Prop", "White_Prop")
QC_demo_stats <- matrix(
  ncol = length(col_names),
  nrow = length(row_names),
  dimnames = list(row_names, col_names)
)

#median Fd
avg_med_fd_PNC <- mean(demo_PNC$median_fd_combined)
QC_demo_stats[1,1] <- avg_med_fd_PNC
avg_med_fd_22q <- mean(demo_22q$median_fd_combined)
QC_demo_stats[1,3] <- avg_med_fd_22q

sd_med_fd_PNC <- sd(demo_PNC$median_fd_combined)
QC_demo_stats[1,2] <- sd_med_fd_PNC
sd_med_fd_22q <- sd(demo_22q$median_fd_combined)
QC_demo_stats[1,4] <- sd_med_fd_22q

med_fd_t_test <- t.test(demo_PNC$median_fd_combined, demo_22q$median_fd_combined, alternative = "two.sided", var.equal = FALSE)
med_fd_t_val <- med_fd_t_test$statistic
med_fd_p_val <- med_fd_t_test$p.value
QC_demo_stats[1,5] <- med_fd_p_val


#Euler
avg_euler_PNC <- mean(demo_PNC$euler)
QC_demo_stats[2,1] <- avg_euler_PNC
avg_euler_22q <- mean(demo_22q$euler)
QC_demo_stats[2,3] <- avg_euler_22q

sd_euler_PNC <- sd(demo_PNC$euler)
QC_demo_stats[2,2] <- sd_euler_PNC
sd_euler_22q <- sd(demo_22q$euler)
QC_demo_stats[2,4] <- sd_euler_22q

euler_t_test <- t.test(demo_PNC$euler, demo_22q$euler, alternative = "two.sided", var.equal = FALSE)
euler_t_val <- euler_t_test$statistic
euler_p_val <- euler_t_test$p.value
QC_demo_stats[2,5] <- euler_p_val

#Age
avg_age_PNC <- mean(demo_PNC$age)
QC_demo_stats[3,1] <- avg_age_PNC
avg_age_22q <- mean(demo_22q$age)
QC_demo_stats[3,3] <- avg_age_22q

sd_age_PNC <- sd(demo_PNC$age)
QC_demo_stats[3,2] <- sd_age_PNC
sd_age_22q <- sd(demo_22q$age)
QC_demo_stats[3,4] <- sd_age_22q

age_t_test <- t.test(demo_PNC$age, demo_22q$age, alternative = "two.sided", var.equal = FALSE)
age_t_val <- age_t_test$statistic
age_p_val <- age_t_test$p.value
QC_demo_stats[3,5] <- age_p_val

#Visualize age distribution
Fig <- ggplot(demo_PNC, aes(x = age)) +
  geom_histogram(binwidth = 2,    # Width of the bins
                 fill = "black", # Fill color of the bars
                 color = "black") + # Border color of the bars
  geom_histogram(data = demo_22q, aes(x = age), 
                 binwidth = 2,    # Width of the bins
                 fill = "gray", # Fill color of the bars
                 color = "gray", # Border color of the bars
                 alpha = 0.7) + 
  labs(title = paste0("PNC vs 22q11.2DS Age Distribution"),
       x = "Age)",
       y = "Number of Subjects") +
  theme(plot.title = element_text(hjust = 0.5))
print(Fig)

#Sex
N_female_PNC <- sum(demo_PNC$sex == "Female")
N_PNC <- nrow(demo_PNC)
female_prop_PNC <- N_female_PNC/N_PNC
QC_demo_stats[4,1] <- female_prop_PNC

N_female_22q <- sum(demo_22q$sex == "Female")
N_22q <- nrow(demo_22q)
female_prop_22q <- N_female_22q/N_22q
QC_demo_stats[4,3] <- female_prop_22q

N_females <- c(N_female_PNC, N_female_22q)
N_samples <- c(N_PNC, N_22q)

female_prop_test <- prop.test(N_females, N_samples, correct = FALSE)
female_prop_X <- female_prop_test$statistic
female_prop_p_val <- female_prop_test$p.value
QC_demo_stats[4,5] <- female_prop_p_val


#Race
N_White_PNC <- sum(demo_PNC$race == "White")
N_PNC <- nrow(demo_PNC)
White_prop_PNC <- N_White_PNC/N_PNC
QC_demo_stats[5,1] <- White_prop_PNC

N_White_22q <- sum(demo_22q$race == "White")
N_22q <- nrow(demo_22q)
White_prop_22q <- N_White_22q/N_22q
QC_demo_stats[5,3] <- White_prop_22q

N_Whites <- c(N_White_PNC, N_White_22q)
N_samples <- c(N_PNC, N_22q)

White_prop_test <- prop.test(N_Whites, N_samples, correct = FALSE)
White_prop_X <- White_prop_test$statistic
White_prop_p_val <- White_prop_test$p.value
QC_demo_stats[5,5] <- White_prop_p_val

write.csv(QC_demo_stats,'C:/Users/kevin/OneDrive/Documents/NGG_PhD/Alexander-Bloch/22q_Project/Analyses/Results/Demographic_matching/PNC_22q_demo_QC_stats.csv', row.names = TRUE)

```

------------------------------
Create Matched Data
------------------------------

#Merge 22q and PNC for matching purposes
```{r}
demo_22q$stat_22q <- 1
demo_PNC$stat_22q <- 0
colnames(demo_PNC)[1] <- "subject"

demo_22q$subject <- gsub("sub-0", "", demo_22q$subject)
demo_22q$subject <- gsub("sub-", "", demo_22q$subject)

demo_22q_keep <- demo_22q[,c("subject","stat_22q","age","sex","race","median_fd_combined","euler")]
demo_PNC_keep <- demo_PNC[,c("subject","stat_22q","age","sex","race","median_fd_combined","euler")]

#Pool 2 datasets
PNC_22q_pooled <- rbind(demo_22q_keep,demo_PNC_keep) #N = 1432

# Pool "Asian" and "Mixed" into "Other" for race
PNC_22q_pooled$race <- gsub("Asian", "Other", PNC_22q_pooled$race)
PNC_22q_pooled$race <- gsub("Mixed", "Other", PNC_22q_pooled$race)
```


# 1. Match 1 to 1 with median fd
```{r}
m_r1_fd <- matchit(stat_22q ~ age + sex + race + median_fd_combined,
                  data = PNC_22q_pooled,
                  method = "nearest",
                  ratio = 1,
                  caliper = 0.1,
                  distance = "glm")

summary(m_r1_fd)
plot(summary(m_r1_fd))
matched_r1 <- match.data(m_r1_fd)
```

# 2. Match 1 to 1 with median fd again after removing round 1 matched controls
```{r}
drop_subj <- matched_r1$subject[matched_r1$stat_22q == 0]

PNC_22q_pooled_post_r1 <- PNC_22q_pooled[!(PNC_22q_pooled$subject %in% drop_subj),]

m_r1.2_fd <- matchit(stat_22q ~ age + sex + race + median_fd_combined,
                  data = PNC_22q_pooled_post_r1,
                  method = "nearest",
                  ratio = 1,
                  caliper = 0.1,
                  distance = "glm")

summary(m_r1.2_fd)
plot(summary(m_r1.2_fd))
matched_r1.2 <- match.data(m_r1.2_fd)
```


# 3. Match 1 to 1 with median fd again after removing round 2 matched controls
```{r}
drop_subj <- matched_r1.2$subject[matched_r1.2$stat_22q == 0]

PNC_22q_pooled_post_r1.2 <- PNC_22q_pooled_post_r1[!(PNC_22q_pooled_post_r1$subject %in% drop_subj),]

m_r1.3_fd <- matchit(stat_22q ~ age + sex + race + median_fd_combined,
                  data = PNC_22q_pooled_post_r1.2,
                  method = "nearest",
                  ratio = 1,
                  caliper = 0.1,
                  distance = "glm")

summary(m_r1.3_fd)
plot(summary(m_r1.3_fd))
matched_r1.3 <- match.data(m_r1.3_fd)
```

#Pool after 3 rounds of matching and save out matched sample (ratio 1 x3, with median FD- use matched case to define subclasses)
```{r}
matched_r1$match_round <- 1
matched_r1.2$match_round <- 2
matched_r1.3$match_round <- 3

attach_case_id <- function(dat, round_num) { # use matched case to define subclasses

  case_lookup <- dat %>%
    filter(stat_22q == 1) %>%
    select(
      subclass,
      matched_case = subject
    )

  dat %>%
    left_join(case_lookup, by = "subclass") %>%
    mutate(match_round = round_num)
}

matched_r1   <- attach_case_id(matched_r1,   1)
matched_r1.2 <- attach_case_id(matched_r1.2, 2)
matched_r1.3 <- attach_case_id(matched_r1.3, 3)

matched_all <- bind_rows(
  matched_r1,
  matched_r1.2,
  matched_r1.3
) %>%
  arrange(subject, match_round) %>% # priority: round 1 then 2 then 3
  group_by(subject) %>%
  slice(1) %>%                      # keep the earliest match case
  ungroup()

matched_all <- matched_all %>%
  mutate(
    subclass = factor(matched_case)
  )

subclass_check <- matched_all %>%
  group_by(subclass) %>%
  summarise(
    n_case = sum(stat_22q == 1),
    n_control = sum(stat_22q == 0),
    .groups = "drop"
  )

subclass_check %>%
  filter(
    n_case != 1 |
    n_control < 1 |
    n_control > 3
  )

write.csv(matched_all,'C:/Users/kevin/OneDrive/Documents/NGG_PhD/Alexander-Bloch/22q_Project/Analyses/Results/Demographic_matching/matched_all_demo_QC_median_fd_r1x3.csv', row.names = FALSE)
```


# calculate stats after matching
```{r}

# ------------------------------------------------------------
# Helper functions
# ------------------------------------------------------------

# Standardized mean difference for continuous variables:
# 22q minus PNC, divided by pooled SD
smd_continuous <- function(x_control, x_22q) {

  m0 <- mean(x_control, na.rm = TRUE)
  m1 <- mean(x_22q, na.rm = TRUE)

  sd0 <- sd(x_control, na.rm = TRUE)
  sd1 <- sd(x_22q, na.rm = TRUE)

  pooled_sd <- sqrt((sd0^2 + sd1^2) / 2)

  if (pooled_sd == 0) {
    return(NA_real_)
  }

  (m1 - m0) / pooled_sd
}


# Standardized mean difference for binary variables:
# 22q minus PNC
smd_binary <- function(p_control, p_22q) {

  pooled_sd <- sqrt(
    (
      p_control * (1 - p_control) +
      p_22q * (1 - p_22q)
    ) / 2
  )

  if (pooled_sd == 0) {
    return(NA_real_)
  }

  (p_22q - p_control) / pooled_sd
}


# ------------------------------------------------------------
# Initialize demographic/QC table
# ------------------------------------------------------------

col_names <- c(
  "PNC",
  "SD_PNC",
  "22q",
  "SD_22q",
  "p_value",
  "SMD",
  "Abs_SMD"
)

row_names <- c(
  "Median_FD",
  "Age",
  "Female_Prop",
  "White_Prop",
  "Black_Prop",
  "Other_Prop"
)

QC_demo_stats_matched_all <- matrix(
  NA_real_,
  ncol = length(col_names),
  nrow = length(row_names),
  dimnames = list(row_names, col_names)
)


# ------------------------------------------------------------
# Sample sizes
# ------------------------------------------------------------

N_controls <- sum(matched_all$stat_22q == 0)
N_22q <- sum(matched_all$stat_22q == 1)

cat("PNC controls:", N_controls, "\n")
cat("22q cases:", N_22q, "\n")


# ------------------------------------------------------------
# Continuous variables
# ------------------------------------------------------------

continuous_vars <- c(
  "median_fd_combined",
  "age"
)

continuous_rows <- c(
  "Median_FD",
  "Age"
)

for (i in seq_along(continuous_vars)) {

  var <- continuous_vars[i]
  row <- continuous_rows[i]

  x_control <- matched_all[
    matched_all$stat_22q == 0,
    var,
    drop = TRUE
  ]

  x_22q <- matched_all[
    matched_all$stat_22q == 1,
    var,
    drop = TRUE
  ]

  # Group summaries
  QC_demo_stats_matched_all[row, "PNC"] <-
    mean(x_control, na.rm = TRUE)

  QC_demo_stats_matched_all[row, "SD_PNC"] <-
    sd(x_control, na.rm = TRUE)

  QC_demo_stats_matched_all[row, "22q"] <-
    mean(x_22q, na.rm = TRUE)

  QC_demo_stats_matched_all[row, "SD_22q"] <-
    sd(x_22q, na.rm = TRUE)

  # Welch t-test
  test <- t.test(
    x_control,
    x_22q,
    alternative = "two.sided",
    var.equal = FALSE
  )

  QC_demo_stats_matched_all[row, "p_value"] <-
    test$p.value

  # Standardized mean difference
  smd <- smd_continuous(
    x_control,
    x_22q
  )

  QC_demo_stats_matched_all[row, "SMD"] <- smd
  QC_demo_stats_matched_all[row, "Abs_SMD"] <- abs(smd)
}


# ------------------------------------------------------------
# Sex: Female proportion
# ------------------------------------------------------------

N_female_control <- sum(
  matched_all$stat_22q == 0 &
    matched_all$sex == "Female",
  na.rm = TRUE
)

N_female_22q <- sum(
  matched_all$stat_22q == 1 &
    matched_all$sex == "Female",
  na.rm = TRUE
)

female_prop_control <-
  N_female_control / N_controls

female_prop_22q <-
  N_female_22q / N_22q


QC_demo_stats_matched_all[
  "Female_Prop",
  "PNC"
] <- female_prop_control

QC_demo_stats_matched_all[
  "Female_Prop",
  "22q"
] <- female_prop_22q


female_test <- prop.test(
  x = c(
    N_female_control,
    N_female_22q
  ),
  n = c(
    N_controls,
    N_22q
  ),
  correct = FALSE
)

QC_demo_stats_matched_all[
  "Female_Prop",
  "p_value"
] <- female_test$p.value


female_smd <- smd_binary(
  female_prop_control,
  female_prop_22q
)

QC_demo_stats_matched_all[
  "Female_Prop",
  "SMD"
] <- female_smd

QC_demo_stats_matched_all[
  "Female_Prop",
  "Abs_SMD"
] <- abs(female_smd)


# ------------------------------------------------------------
# Race category proportions
# ------------------------------------------------------------

race_levels <- c(
  "White",
  "Black",
  "Other"
)

race_rows <- paste0(
  race_levels,
  "_Prop"
)

for (i in seq_along(race_levels)) {

  race_level <- race_levels[i]
  row <- race_rows[i]

  n_control <- sum(
    matched_all$stat_22q == 0 &
      matched_all$race == race_level,
    na.rm = TRUE
  )

  n_22q <- sum(
    matched_all$stat_22q == 1 &
      matched_all$race == race_level,
    na.rm = TRUE
  )

  prop_control <- n_control / N_controls
  prop_22q <- n_22q / N_22q


  QC_demo_stats_matched_all[
    row,
    "PNC"
  ] <- prop_control

  QC_demo_stats_matched_all[
    row,
    "22q"
  ] <- prop_22q


  # Category-specific proportion test
  prop_test <- prop.test(
    x = c(n_control, n_22q),
    n = c(N_controls, N_22q),
    correct = FALSE
  )

  QC_demo_stats_matched_all[
    row,
    "p_value"
  ] <- prop_test$p.value


  # Category-specific SMD
  smd <- smd_binary(
    prop_control,
    prop_22q
  )

  QC_demo_stats_matched_all[
    row,
    "SMD"
  ] <- smd

  QC_demo_stats_matched_all[
    row,
    "Abs_SMD"
  ] <- abs(smd)
}


# ------------------------------------------------------------
# Omnibus race comparison
# ------------------------------------------------------------

race_table <- table(
  matched_all$stat_22q,
  matched_all$race
)

race_omnibus_test <- chisq.test(
  race_table,
  correct = FALSE
)

race_omnibus_p <- race_omnibus_test$p.value

cat(
  "Omnibus race p-value:",
  race_omnibus_p,
  "\n"
)


# ------------------------------------------------------------
# Final balance table
# ------------------------------------------------------------

QC_demo_stats_matched_all <-
  as.data.frame(QC_demo_stats_matched_all)

write.csv(QC_demo_stats_matched_all,'C:/Users/kevin/OneDrive/Documents/NGG_PhD/Alexander-Bloch/22q_Project/Analyses/Results/Demographic_matching/stats_matched_all_demo_QC_median_fd_r1x3.csv', row.names = TRUE)
```
