---
title: "Models_22q_PFN"
author: "Kevin Sun"
date: "`1/20/2026`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
library(readr)
library(sjPlot)
library(mgcv)
```

#Import areas and demographics
```{r}
#Read in area data
areas_PNC <- read.csv("../../Inputs/PNC_summary_PFNs.csv") # n = 1482
colnames(areas_PNC) <- gsub("_soft_parcel_normed", "", colnames(areas_PNC))
areas_22q <- read.csv("../../Inputs/22q_summary_PFNs.csv") # n = 115
areas_22q <- areas_22q[areas_22q$session != 8971,] #Remove ses-008971 of sub-016095, since this subject has 2 sessions -> n = 114

#Pool 22q and PNC area data
areas_22q <- areas_22q[, -2] #remove session column
areas_all <- rbind(areas_PNC,areas_22q) # n = 1596

#merge pooled areas with matched and pooled demographic dataset
matched_demo <- read.csv("../../Results/Demographic_matching/matched_all_demo_QC_median_fd_r1x3.csv") # n = 215
matched_all <- merge(matched_demo,areas_all,by="subject") # n = 215

#write_csv(matched_all,paste0("../../Inputs/22q_PNC_matched_all.csv"))

PFN_names <- c("DM-B", "SM-foot", "FP-A", "SM-face", "DA-post", "VS-peri", "Salience", "Language", "CingOp", "VS-cent", "SM-lh", "DM-A", "SM-rh", "DA-ant", "ParMem", "Auditory", "FP-B")
```

#Factorize 22q status and sex
```{r}
matched_all$stat_22q <- factor(matched_all$stat_22q)
matched_all$sex <- factor(matched_all$sex)
matched_all$subclass <- factor(matched_all$subclass)
```


## 22q with euler + age spline, no TC_area
```{r}
dout <- "../../Results/22q_PFN_Age/No_TCA/subclass"
dir.create(dout)

models_no_TCA <- list()

for (net in c(1:17)) {
  PFN_area <- sprintf("PFN%02d",net)
  model_no_TCA <- gam(log(get(PFN_area)) ~ stat_22q+sex+euler+median_fd_combined+s(age,k=4)+s(subclass, bs = "re"),data=matched_all,method = "REML")
  print(tab_model(model_no_TCA,dv.labels=c(paste0("PFN ",net, " Area")),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = paste0(dout,"/22q_PFN_no_TCA_PFN_",net,"_REML_subclass.doc")))
  models_no_TCA[[net]] <- model_no_TCA #store all models in list
}

```

# Save out betas and bonf p-vals of 22q term (no TCA)
```{r}
dout <- "../../Results/22q_PFN_Age/No_TCA/subclass"

no_TCA_mod_results <- matrix(0,17,2)

for (net in c(1:17)) {
  net_model <- models_no_TCA[[net]]
  no_TCA_mod_results[net,1] <- summary(net_model)$p.table["stat_22q1", "Estimate"]
  no_TCA_mod_results[net,2] <- summary(net_model)$p.table["stat_22q1", "Pr(>|t|)"]
}

pvals_bonf <- p.adjust(no_TCA_mod_results[,2], method = "bonf")
#PFN_names <- c("PFN1", "PFN2", "PFN3", "PFN4", "PFN5", "PFN6", "PFN7", "PFN8", "PFN9", "PFN10", "PFN11", "PFN12", "PFN13", "PFN14", "PFN15", "PFN16", "PFN17")
no_TCA_bonf <-  data.frame(PFN = PFN_names, beta = no_TCA_mod_results[,1], pvals_bonf = pvals_bonf)

write_csv(no_TCA_bonf,paste0(dout,"/22q_PFN_no_TCA_summary_results_bonf_REML_subclass.csv"))
```


### Bar plot of 22q effect, no TCA (EXP AND RELATIVE TO 1 * 100):
```{r}
p_vec_adj<- no_TCA_bonf[,3]
print(p_vec_adj)
keep_p <- ifelse(p_vec_adj<.05,1,0)
print(keep_p)

betas <- (exp(no_TCA_bonf[,2])-1)*100 #EXP AND SET RELATIVE TO 1 *100
sorted_beta = rank(betas);
pfn_inAscend_indx <- c()
for (t in c(1:17)) { pfn_inAscend_indx <- append(pfn_inAscend_indx,which(sorted_beta == t))} #if using numbers, switch all pfn_inAscend to pfn_inAscend_indx and comment out next line
pfn_inAscend <- PFN_names[pfn_inAscend_indx]

# Using 7 colors scheme for bar plot
data <- data.frame(EffectSizes = as.numeric(betas)) 
data$EffectRank <- as.numeric(sorted_beta)
# BorderColor1 is for colors of 1-17 network numbers(to lable the network numbers in a 1-17 order)
BorderColor1 <- c("#E76178", "#7499C2", "#F5BA2E", "#7499C2", "#00A131",
                 "#AF33AD", "#E443FF", "#E76178", "#E443FF", "#AF33AD",
                 "#7499C2", "#E76178", "#7499C2", "#00A131", "#F5BA2E", 
                 "#4E31A8", "#F5BA2E");
				 
# BorderColor2 is for colors of bar fill 1-17 networks (in a 1-17 order). If the bar is nofill, change the code to "#FFFFFF" for that PFN. ("black" is filled with black)
BorderColor2 <- c("#FFFFFF", "#FFFFFF", "#FFFFFF", "#FFFFFF", "#00A131",
                 "#AF33AD", "#FFFFFF", "#FFFFFF", "#FFFFFF", "#AF33AD",
                 "#FFFFFF", "#E76178", "#FFFFFF", "#00A131", "#F5BA2E", 
                 "#FFFFFF", "#F5BA2E");

# TextColor is for network label color
TextColor <- c("#767676", "#767676", "#767676", "#767676", "black",
                 "black", "#767676", "#767676", "#767676", "black",
                 "#767676", "black", "#767676", "black", "black", 
                 "#767676", "black");

# Change the color order
BorderColor <- BorderColor1[pfn_inAscend_indx]
BorderColor3 <- BorderColor2[pfn_inAscend_indx]
TextColor_ordered <- TextColor[pfn_inAscend_indx]

Fig <- ggplot(data, aes(EffectRank, EffectSizes)) +
  geom_bar(stat = "identity", fill=BorderColor3[sorted_beta], 
           colour = BorderColor[sorted_beta], linetype = "solid", width = 0.8) + 
  labs(title = NULL, x = NULL, y = paste0("PFN Areal Change (%)")) + theme_classic() +
  theme(plot.title = ggtext::element_markdown(size=25, hjust = 0.5)) +
  theme(axis.text.y = ggtext::element_markdown(size= 21, color = TextColor_ordered), 
        axis.text.x = ggtext::element_markdown(size= 25, color = "black"), 
        axis.title=ggtext::element_markdown(size = 25)) +
  #theme(axis.text.x = ggtext::element_markdown(angle = 45, hjust = 1)) +
  scale_x_discrete(labels = as.character(pfn_inAscend),limits = as.character(sorted_beta)) +
  scale_y_continuous(limits = c(-11, 0)) +
  coord_flip()

Fig
ggsave(paste0("../../Results/22q_PFN_Age/No_TCA/subclass/22q_PFN_no_TCA_plot_REML_bonf_EXP_REL_100perc_subclass.png"), width = 19, height = 16, dpi = 600, units = "cm");
ggsave(paste0("../../Results/22q_PFN_Age/No_TCA/subclass/22q_PFN_no_TCA_plot_REML_bonf_EXP_REL_100perc_subclass.pdf"), device = cairo_pdf, width = 19, height = 16, dpi = 600, units = "cm")
```


## 22q with TCA + euler + age spline
```{r}
dout <- "../../Results/22q_PFN_Age/subclass"
dir.create(dout)

models_TCA_euler_age <- list()

for (net in c(1:17)) {
  PFN_area <- sprintf("PFN%02d",net)
  model_TCA_euler_age <- gam(log(get(PFN_area)) ~ stat_22q+log(TC_area)+sex+euler+median_fd_combined+s(age,k=4)+s(subclass, bs = "re"),data=matched_all,method = "REML")
  print(tab_model(model_TCA_euler_age,dv.labels=c(paste0("PFN ",net, " Area")),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = paste0(dout,"/22q_PFN_TCA_euler_age_PFN_",net,"_REML_subclass.doc")))
  models_TCA_euler_age[[net]] <- model_TCA_euler_age #store all models in list
}
```

# Save out betas and bonf p-vals of 22q term
```{r}
dout <- "../../Results/22q_PFN_Age/subclass"

TCA_euler_age_mod_results <- matrix(0,17,2)

for (net in c(1:17)) {
  net_model <- models_TCA_euler_age[[net]]
  TCA_euler_age_mod_results[net,1] <- summary(net_model)$p.table["stat_22q1", "Estimate"]
  TCA_euler_age_mod_results[net,2] <- summary(net_model)$p.table["stat_22q1", "Pr(>|t|)"]
}

pvals_bonf <- p.adjust(TCA_euler_age_mod_results[,2], method = "bonf")
#PFN_names <- c("PFN1", "PFN2", "PFN3", "PFN4", "PFN5", "PFN6", "PFN7", "PFN8", "PFN9", "PFN10", "PFN11", "PFN12", "PFN13", "PFN14", "PFN15", "PFN16", "PFN17")
TCA_euler_age_bonf <-  data.frame(PFN = PFN_names, beta = TCA_euler_age_mod_results[,1], pvals_bonf = pvals_bonf)

write_csv(TCA_euler_age_bonf,paste0(dout,"/22q_PFN_TCA_euler_age_summary_results_bonf_REML_subclass.csv"))
```


### Bar plot of 22q effect, TCA + euler + age (EXP AND REL TO 1 * 100):
```{r}
p_vec_adj<- TCA_euler_age_bonf[,3]
print(p_vec_adj)
keep_p <- ifelse(p_vec_adj<.05,1,0)
print(keep_p)

betas <- (exp(TCA_euler_age_bonf[,2])-1)*100 # EXP AND REL TO 1 * 100
sorted_beta = rank(betas);
pfn_inAscend_indx <- c()
for (t in c(1:17)) { pfn_inAscend_indx <- append(pfn_inAscend_indx,which(sorted_beta == t))} #if using numbers, switch all pfn_inAscend to pfn_inAscend_indx and comment out next line
pfn_inAscend <- PFN_names[pfn_inAscend_indx]

# Using 7 colors scheme for bar plot
data <- data.frame(EffectSizes = as.numeric(betas)) 
data$EffectRank <- as.numeric(sorted_beta)
# BorderColor1 is for colors of 1-17 network numbers(to lable the network numbers in a 1-17 order)
BorderColor1 <- c("#E76178", "#7499C2", "#F5BA2E", "#7499C2", "#00A131",
                 "#AF33AD", "#E443FF", "#E76178", "#E443FF", "#AF33AD",
                 "#7499C2", "#E76178", "#7499C2", "#00A131", "#F5BA2E", 
                 "#4E31A8", "#F5BA2E");
				 
# BorderColor2 is for colors of bar fill 1-17 networks (in a 1-17 order). If the bar is nofill, change the code to "#FFFFFF" for that PFN. ("black" is filled with black)
BorderColor2 <- c("#FFFFFF", "#FFFFFF", "#FFFFFF", "#FFFFFF", "#FFFFFF",
                 "#AF33AD", "#FFFFFF", "#FFFFFF", "#E443FF", "#FFFFFF",
                 "#FFFFFF", "#FFFFFF", "#FFFFFF", "#FFFFFF", "#FFFFFF", 
                 "#FFFFFF", "#FFFFFF");

# TextColor is for network label color
TextColor <- c("#767676", "#767676", "#767676", "#767676", "#767676",
                 "black", "#767676", "#767676", "black", "#767676",
                 "#767676", "#767676", "#767676", "#767676", "#767676", 
                 "#767676", "#767676");

# Change the color order
BorderColor <- BorderColor1[pfn_inAscend_indx]
BorderColor3 <- BorderColor2[pfn_inAscend_indx]
TextColor_ordered <- TextColor[pfn_inAscend_indx]

Fig <- ggplot(data, aes(EffectRank, EffectSizes)) +
  geom_bar(stat = "identity", fill=BorderColor3[sorted_beta], 
           colour = BorderColor[sorted_beta], linetype = "solid", width = 0.8) + 
  labs(title = NULL, x = NULL, y = paste0("PFN Areal Change (%)")) + theme_classic() +
  theme(plot.title = ggtext::element_markdown(size=25, hjust = 0.5)) +
  theme(axis.text.y = ggtext::element_markdown(size= 21, color = TextColor_ordered), 
        axis.text.x = ggtext::element_markdown(size= 25, color = "black"), 
        axis.title=ggtext::element_markdown(size = 25)) +
  #theme(axis.text.x = ggtext::element_markdown(angle = 45, hjust = 1)) +
  scale_x_discrete(labels = as.character(pfn_inAscend),limits = as.character(sorted_beta)) +
  scale_y_continuous(limits = c(-6, 5)) +
  coord_flip()

Fig
ggsave(paste0("../../Results/22q_PFN_Age/subclass/22q_PFN_TCA_euler_age_plot_REML_bonf_EXP_REL_100perc_subclass.png"), width = 19, height = 16, dpi = 600, units = "cm");
ggsave(paste0("../../Results/22q_PFN_Age/subclass/22q_PFN_TCA_euler_age_plot_REML_bonf_EXP_REL_100perc_subclass.pdf"), device = cairo_pdf, width = 19, height = 16, dpi = 600, units = "cm");
```


## models 22q, no age spline
```{r}

models_no_age <- list()

for (net in c(1:17)) {
  PFN_area <- sprintf("PFN%02d",net)
  model_no_age <- gam(log(get(PFN_area)) ~ stat_22q+log(TC_area)+sex+euler+median_fd_combined+s(subclass, bs = "re"),data=matched_all,method = "REML")
  models_no_age[[net]] <- model_no_age #store all models in list
}

```

# Save out betas and bonf p-vals of 22q term (no age)
```{r}
dout <- "../../Results/22q_PFN_No_age/subclass"
dir.create(dout)

no_age_mod_results <- matrix(0,17,2)

for (net in c(1:17)) {
  net_model <- models_no_age[[net]]
  no_age_mod_results[net,1] <- summary(net_model)$p.table["stat_22q1", "Estimate"]
  no_age_mod_results[net,2] <- summary(net_model)$p.table["stat_22q1", "Pr(>|t|)"]
}

pvals_bonf <- p.adjust(no_age_mod_results[,2], method = "bonf")
#PFN_names <- c("PFN1", "PFN2", "PFN3", "PFN4", "PFN5", "PFN6", "PFN7", "PFN8", "PFN9", "PFN10", "PFN11", "PFN12", "PFN13", "PFN14", "PFN15", "PFN16", "PFN17")
no_age_bonf <-  data.frame(PFN = PFN_names, beta = no_age_mod_results[,1], pvals_bonf = pvals_bonf)

write_csv(no_age_bonf,paste0(dout,"/22q_PFN_TCA_no_age_summary_results_bonf_REML_subclass.csv"))
```

### Bar plot of 22q effect, no age:
```{r}
p_vec_adj<- no_age_bonf[,3]
print(p_vec_adj)
keep_p <- ifelse(p_vec_adj<.05,1,0)
print(keep_p)

betas <- (exp(no_age_bonf[,2]) -1)*100 # EXP AND REL TO 1 * 100 for percent
sorted_beta = rank(betas);
pfn_inAscend_indx <- c()
for (t in c(1:17)) { pfn_inAscend_indx <- append(pfn_inAscend_indx,which(sorted_beta == t))} #if using numbers, switch all pfn_inAscend to pfn_inAscend_indx and comment out next line
pfn_inAscend <- PFN_names[pfn_inAscend_indx]

# Using 7 colors scheme for bar plot
data <- data.frame(EffectSizes = as.numeric(betas)) 
data$EffectRank <- as.numeric(sorted_beta)
# BorderColor1 is for colors of 1-17 network numbers(to lable the network numbers in a 1-17 order)
BorderColor1 <- c("#E76178", "#7499C2", "#F5BA2E", "#7499C2", "#00A131",
                 "#AF33AD", "#E443FF", "#E76178", "#E443FF", "#AF33AD",
                 "#7499C2", "#E76178", "#7499C2", "#00A131", "#F5BA2E", 
                 "#4E31A8", "#F5BA2E");
				 
# BorderColor2 is for colors of bar fill 1-17 networks (in a 1-17 order). If the bar is nofill, change the code to "#FFFFFF" for that PFN. ("black" is filled with black)
BorderColor2 <- c("#FFFFFF", "#FFFFFF", "#FFFFFF", "#FFFFFF", "#FFFFFF",
                 "#AF33AD", "#FFFFFF", "#FFFFFF", "#E443FF", "#FFFFFF",
                 "#FFFFFF", "#FFFFFF", "#FFFFFF", "#FFFFFF", "#FFFFFF", 
                 "#FFFFFF", "#FFFFFF");

# TextColor is for network label color
TextColor <- c("#767676", "#767676", "#767676", "#767676", "#767676",
                 "black", "#767676", "#767676", "black", "#767676",
                 "#767676", "#767676", "#767676", "#767676", "#767676", 
                 "#767676", "#767676");

# Change the color order
BorderColor <- BorderColor1[pfn_inAscend_indx]
BorderColor3 <- BorderColor2[pfn_inAscend_indx]
TextColor_ordered <- TextColor[pfn_inAscend_indx]

Fig <- ggplot(data, aes(EffectRank, EffectSizes)) +
  geom_bar(stat = "identity", fill=BorderColor3[sorted_beta], 
           colour = BorderColor[sorted_beta], linetype = "solid", width = 0.8) + 
  labs(title = NULL, x = NULL, y = paste0("PFN Areal Change (%)")) + theme_classic() +
  theme(plot.title = ggtext::element_markdown(size=25, hjust = 0.5)) +
  theme(axis.text.y = ggtext::element_markdown(size= 21, color = TextColor_ordered), 
        axis.text.x = ggtext::element_markdown(size= 25, color = "black"), 
        axis.title=ggtext::element_markdown(size = 25)) +
  #theme(axis.text.x = ggtext::element_markdown(angle = 45, hjust = 1)) +
  scale_x_discrete(labels = as.character(pfn_inAscend),limits = as.character(sorted_beta)) +
  scale_y_continuous(limits = c(-6, 5)) +
  coord_flip()

Fig
ggsave(paste0("../../Results/22q_PFN_No_Age/subclass/22q_PFN_TCA_no_age_plot_REML_bonf_EXP_REL_100perc_subclass.png"), width = 19, height = 16, dpi = 600, units = "cm");
ggsave(paste0("../../Results/22q_PFN_No_Age/subclass/22q_PFN_TCA_no_age_plot_REML_bonf_EXP_REL_100perc_subclass.pdf"), device = cairo_pdf, width = 19, height = 16, dpi = 600, units = "cm");
```


## models 22q, no euler
```{r}
models_no_euler <- list()

for (net in c(1:17)) {
  PFN_area <- sprintf("PFN%02d",net)
  model_no_euler <- gam(log(get(PFN_area)) ~ stat_22q+log(TC_area)+sex+median_fd_combined+s(age,k=4)+s(subclass, bs = "re"),data=matched_all,method = "REML")
  models_no_euler[[net]] <- model_no_euler #store all models in list
}

```

# Save out betas and bonf p-vals of 22q term (no euler)
```{r}
dout <- "../../Results/22q_PFN_Age/No_euler/subclass"
dir.create(dout)

no_euler_mod_results <- matrix(0,17,2)

for (net in c(1:17)) {
  net_model <- models_no_euler[[net]]
  no_euler_mod_results[net,1] <- summary(net_model)$p.table["stat_22q1", "Estimate"]
  no_euler_mod_results[net,2] <- summary(net_model)$p.table["stat_22q1", "Pr(>|t|)"]
}

pvals_bonf <- p.adjust(no_euler_mod_results[,2], method = "bonf")
#PFN_names <- c("PFN1", "PFN2", "PFN3", "PFN4", "PFN5", "PFN6", "PFN7", "PFN8", "PFN9", "PFN10", "PFN11", "PFN12", "PFN13", "PFN14", "PFN15", "PFN16", "PFN17")
no_euler_bonf <-  data.frame(PFN = PFN_names, beta = no_euler_mod_results[,1], pvals_bonf = pvals_bonf)

write_csv(no_euler_bonf,paste0(dout,"/22q_PFN_TCA_no_euler_summary_results_bonf_REML_subclass.csv"))
```

### Bar plot of 22q effect, no euler:
```{r}
p_vec_adj<- no_euler_bonf[,3]
print(p_vec_adj)
keep_p <- ifelse(p_vec_adj<.05,1,0)
print(keep_p)

betas <- (exp(no_euler_bonf[,2]) -1)*100 # EXP AND REL TO 1 * 100 for percent
sorted_beta = rank(betas);
pfn_inAscend_indx <- c()
for (t in c(1:17)) { pfn_inAscend_indx <- append(pfn_inAscend_indx,which(sorted_beta == t))} #if using numbers, switch all pfn_inAscend to pfn_inAscend_indx and comment out next line
pfn_inAscend <- PFN_names[pfn_inAscend_indx]

# Using 7 colors scheme for bar plot
data <- data.frame(EffectSizes = as.numeric(betas)) 
data$EffectRank <- as.numeric(sorted_beta)
# BorderColor1 is for colors of 1-17 network numbers(to lable the network numbers in a 1-17 order)
BorderColor1 <- c("#E76178", "#7499C2", "#F5BA2E", "#7499C2", "#00A131",
                 "#AF33AD", "#E443FF", "#E76178", "#E443FF", "#AF33AD",
                 "#7499C2", "#E76178", "#7499C2", "#00A131", "#F5BA2E", 
                 "#4E31A8", "#F5BA2E");
				 
# BorderColor2 is for colors of bar fill 1-17 networks (in a 1-17 order). If the bar is nofill, change the code to "#FFFFFF" for that PFN. ("black" is filled with black)
BorderColor2 <- c("#FFFFFF", "#FFFFFF", "#FFFFFF", "#FFFFFF", "#FFFFFF",
                 "#AF33AD", "#FFFFFF", "#FFFFFF", "#E443FF", "#FFFFFF",
                 "#FFFFFF", "#FFFFFF", "#FFFFFF", "#FFFFFF", "#FFFFFF", 
                 "#FFFFFF", "#FFFFFF");

# TextColor is for network label color
TextColor <- c("#767676", "#767676", "#767676", "#767676", "#767676",
                 "black", "#767676", "#767676", "black", "#767676",
                 "#767676", "#767676", "#767676", "#767676", "#767676", 
                 "#767676", "#767676");

# Change the color order
BorderColor <- BorderColor1[pfn_inAscend_indx]
BorderColor3 <- BorderColor2[pfn_inAscend_indx]
TextColor_ordered <- TextColor[pfn_inAscend_indx]

Fig <- ggplot(data, aes(EffectRank, EffectSizes)) +
  geom_bar(stat = "identity", fill=BorderColor3[sorted_beta], 
           colour = BorderColor[sorted_beta], linetype = "solid", width = 0.8) + 
  labs(title = NULL, x = NULL, y = paste0("PFN Areal Change (%)")) + theme_classic() +
  theme(plot.title = ggtext::element_markdown(size=25, hjust = 0.5)) +
  theme(axis.text.y = ggtext::element_markdown(size= 21, color = TextColor_ordered), 
        axis.text.x = ggtext::element_markdown(size= 25, color = "black"), 
        axis.title=ggtext::element_markdown(size = 25)) +
  #theme(axis.text.x = ggtext::element_markdown(angle = 45, hjust = 1)) +
  scale_x_discrete(labels = as.character(pfn_inAscend),limits = as.character(sorted_beta)) +
  scale_y_continuous(limits = c(-6, 5)) +
  coord_flip()

Fig
ggsave(paste0("../../Results/22q_PFN_Age/No_euler/subclass/22q_PFN_TCA_no_euler_plot_REML_bonf_EXP_REL_100perc_subclass.png"), width = 19, height = 16, dpi = 600, units = "cm"); 
ggsave(paste0("../../Results/22q_PFN_Age/No_euler/subclass/22q_PFN_TCA_no_euler_plot_REML_bonf_EXP_REL_100perc_subclass.pdf"), device = cairo_pdf, width = 19, height = 16, dpi = 600, units = "cm")
```