

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
library(readr)
library(sjPlot)
library(mgcv)
```

#Import areas and demographics
```{r}
#Read in area data
areas_PNC <- read.csv("../../Inputs/PNC_summary_group.csv") # n = 1598
colnames(areas_PNC) <- gsub("_soft_parcel_normed", "", colnames(areas_PNC))
areas_22q <- read.csv("../../Inputs/22q_summary_group.csv") # n = 131
areas_22q <- areas_22q[areas_22q$session != 8971,] #Remove ses-008971 of sub-016095, since this subject has 2 sessions -> n = 130

#Pool 22q and PNC area data
areas_22q <- areas_22q[, -2] #remove session column
areas_all <- rbind(areas_PNC,areas_22q) # n = 1728

#merge pooled areas with matched and pooled demographic dataset
matched_demo <- read.csv("../../Results/Demographic_matching/matched_all_demo_QC_median_fd_r1x3.csv") # n = 215
matched_all <- merge(matched_demo,areas_all,by="subject") # n = 215

PFN_names <- c("DM-B", "SM-foot", "FP-A", "SM-face", "DA-post", "VS-peri", "Salience", "Language", "CingOp", "VS-cent", "SM-lh", "DM-A", "SM-rh", "DA-ant", "ParMem", "Auditory", "FP-B")

```


#Factorize 22q status, subclass, and sex
```{r}
matched_all$stat_22q <- factor(matched_all$stat_22q)
matched_all$sex <- factor(matched_all$sex)
matched_all$subclass <- factor(matched_all$subclass)
```

## 22q status * scaling interaction models
```{r}
dout <- "../../Results/22q_Group_Age/Scaling_Interaction_Models_subclass"
dir.create(dout)

interX_scaling_models <- list()

for (net in c(1:17)) {
  PFN_area <- paste0("PFN",net)
  interX_model <- gam(log(get(PFN_area)) ~stat_22q+log(TC_area)+sex+euler+median_fd_combined+stat_22q*log(TC_area)+s(age,k=4)+s(subclass, bs = "re"),data=matched_all,method = "REML")
  print(tab_model(interX_model,dv.labels=c(paste0("PFN ",net, " Area")),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = paste0(dout,"/Group_22qxTCA_euler_age_PFN_",net,"_REML_subclass.doc")))
  interX_scaling_models[[net]] <- interX_model #store all models in list
}

```


# Save out betas and bonf p-vals of 22q * scaling interaction term
```{r}
dout <- "../../Results/22q_Group_Age/Scaling_Interaction_Models_subclass"

interX_scaling_mod_results <- matrix(0,17,2)

for (net in c(1:17)) {
  net_model <- interX_scaling_models[[net]]
  interX_scaling_mod_results[net,1] <- summary(net_model)$p.table["stat_22q1:log(TC_area)", "Estimate"]
  interX_scaling_mod_results[net,2] <- summary(net_model)$p.table["stat_22q1:log(TC_area)", "Pr(>|t|)"]
}

pvals_bonf <- p.adjust(interX_scaling_mod_results[,2], method = "bonf")
#PFN_names <- c("PFN1", "PFN2", "PFN3", "PFN4", "PFN5", "PFN6", "PFN7", "PFN8", "PFN9", "PFN10", "PFN11", "PFN12", "PFN13", "PFN14", "PFN15", "PFN16", "PFN17")
interX_scaling_bonf <-  data.frame(PFN = PFN_names, beta = interX_scaling_mod_results[,1], pvals_bonf = pvals_bonf)

write_csv(interX_scaling_bonf,paste0(dout,"/Group_22qxTCA_interaction_summary_results_bonf_REML_netnames_subclass.csv"))
```


## Scaling, stratified by 22q status
```{r}
dout <- "../../Results/22q_Group_Age/Scaling_stratified_models_subclass"
dir.create(dout)

del_22q_matched <- matched_all[matched_all$stat_22q == 1, ]
PNC_matched <- matched_all[matched_all$stat_22q == 0, ]

del_22q_scaling_mods <- list()
PNC_scaling_mods <- list()

for (net in c(1:17)) {
  PFN_area <- paste0("PFN",net)
  del_scaling_mod <- gam(log(get(PFN_area))~log(TC_area)+sex+euler+median_fd_combined+s(age,k=4)+s(subclass, bs = "re"),data=del_22q_matched,method = "REML")
  print(tab_model(del_scaling_mod,dv.labels=c(paste0("PFN ",net, " Area")),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = paste0(dout,"/Group_22q_scaling_PFN",net,"_REML_subclass.doc")))
  del_22q_scaling_mods[[net]] <- del_scaling_mod #store all models in list
}

for (net in c(1:17)) {
  PFN_area <- paste0("PFN",net)
  PNC_scaling_mod <- gam(log(get(PFN_area))~log(TC_area)+sex+euler+median_fd_combined+s(age,k=4)+s(subclass, bs = "re"),data=PNC_matched,method = "REML")
  print(tab_model(PNC_scaling_mod,dv.labels=c(paste0("PFN ",net, " Area")),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = paste0(dout,"/Group_PNC_scaling_PFN",net,"_REML_subclass.doc")))
  PNC_scaling_mods[[net]] <- PNC_scaling_mod #store all models in list
}
```

# Get significance of stratified beta scaling terms via Wald test
```{r}
dout <- "../../Results/22q_Group_Age/Scaling_stratified_models_subclass"

del_log_log_results <- matrix(0,17,2)
PNC_log_log_results <- matrix(0,17,2)

for (net in c(1:17)) {
  del_model <- del_22q_scaling_mods[[net]]
  beta <- summary(del_model)$p.table["log(TC_area)", "Estimate"]
  SE <- summary(del_model)$p.table["log(TC_area)", "Std. Error"]
  z_val <- (beta - 1) / SE # Null is beta = 1 (isometry, linear scaling)
  #df <- df.residual(get(paste0("PFN",net,"_gam")))
  del_log_log_results[net,1] <- beta
  del_log_log_results[net,2] <- 2 * (1 - pnorm(abs(z_val))) #Wald test
  
  PNC_model <- PNC_scaling_mods[[net]]
  beta <- summary(PNC_model)$p.table["log(TC_area)", "Estimate"]
  SE <- summary(PNC_model)$p.table["log(TC_area)", "Std. Error"]
  z_val <- (beta - 1) / SE # Null is beta = 1 (isometry, linear scaling)
  #df <- df.residual(get(paste0("PFN",net,"_gam")))
  PNC_log_log_results[net,1] <- beta
  PNC_log_log_results[net,2] <- 2 * (1 - pnorm(abs(z_val))) #Wald test
}

del_pvals_bonf <- p.adjust(del_log_log_results[,2], method = "bonf")
del_log_log_wald_bonf <-  data.frame(PFN = PFN_names, beta = del_log_log_results[,1], pvals_bonf = del_pvals_bonf)

write_csv(del_log_log_wald_bonf,paste0(dout,"/22q_strat_Group_log_log_summary_results_bonf_REML_netnames.csv"))

PNC_pvals_bonf <- p.adjust(PNC_log_log_results[,2], method = "bonf")
PNC_log_log_wald_bonf <-  data.frame(PFN = PFN_names, beta = PNC_log_log_results[,1], pvals_bonf = PNC_pvals_bonf)

write_csv(PNC_log_log_wald_bonf,paste0(dout,"/PNC_strat_Group_log_log_summary_results_bonf_REML_netnames.csv"))
```


# Helper: population-standardized predictions from a GAM
```{r}
# ============================================================
# Helper: population-standardized GAM predictions
# ============================================================

get_standardized_gam_predictions <- function(
    model,
    data,
    focal_var,
    focal_values,
    group_var,
    group_values = NULL,
    exclude_terms = NULL
) {

  if (is.null(group_values)) {
    if (is.factor(data[[group_var]])) {
      group_values <- levels(data[[group_var]])
    } else {
      group_values <- sort(unique(data[[group_var]]))
    }
  }

  beta <- coef(model)
  Vb   <- vcov(model)

  pred_list <- list()
  counter <- 1

  for (g in group_values) {

    for (xval in focal_values) {

      nd <- data

      # ------------------------------------------------------
      # Set focal predictor
      # ------------------------------------------------------

      nd[[focal_var]] <- xval


      # ------------------------------------------------------
      # Set diagnosis variable while preserving its class
      # ------------------------------------------------------

      if (is.ordered(data[[group_var]])) {
      
        nd[[group_var]] <- ordered(
          g,
          levels = levels(data[[group_var]])
        )
      
      } else if (is.factor(data[[group_var]])) {
      
        nd[[group_var]] <- factor(
          g,
          levels = levels(data[[group_var]])
        )
      
      } else {
      
        nd[[group_var]] <- as.numeric(g)
      
      }


      # ------------------------------------------------------
      # Linear predictor matrix
      # ------------------------------------------------------

      X <- predict(
        model,
        newdata = nd,
        type = "lpmatrix",
        exclude = exclude_terms
      )


      # ------------------------------------------------------
      # Population standardization
      # ------------------------------------------------------

      Xbar <- colMeans(X)

      fit <- as.numeric(
        Xbar %*% beta
      )

      se <- sqrt(
        as.numeric(
          Xbar %*% Vb %*% Xbar
        )
      )

      # ------------------------------------------------------
      # Save
      # ------------------------------------------------------

      pred_list[[counter]] <- data.frame(
        x = xval,
        group = as.character(g),
        predicted = fit,
        std.error = se,
        conf.low = fit - 1.96 * se,
        conf.high = fit + 1.96 * se
      )

      counter <- counter + 1
    }
  }

  do.call(rbind, pred_list)
}
```

# Visualize scaling by 22q interaction effect
```{r}
dout <- "../../Results/22q_Group_Age/Scaling_stratified_models_subclass"

# ============================================================
# PFN 3: pooled-model scaling interaction
# ============================================================

net <- 3
PFN_area <- paste0("PFN", net)

model_PFN3_scaling <- interX_scaling_models[[net]]


# ------------------------------------------------------------
# Analysis dataset used by the pooled model
# ------------------------------------------------------------

plot_dat <- matched_all

plot_dat$stat_22q_plot <- as.character(plot_dat$stat_22q)


# ------------------------------------------------------------
# Use common TCA support across groups
#
# This is particularly useful for an interaction plot because
# each pair of fitted curves is evaluated at the same TCA values.
# ------------------------------------------------------------

PNC_tc_range <- range(
  PNC_matched$TC_area,
  na.rm = TRUE
)

del22q_tc_range <- range(
  del_22q_matched$TC_area,
  na.rm = TRUE
)

tc_min_common <- max(
  PNC_tc_range[1],
  del22q_tc_range[1]
)

tc_max_common <- min(
  PNC_tc_range[2],
  del22q_tc_range[2]
)

# Even spacing on the LOG TCA scale because this is a log-log plot
TC_grid <- exp(
  seq(
    log(tc_min_common),
    log(tc_max_common),
    length.out = 100
  )
)


# ------------------------------------------------------------
# Population-standardized predictions from pooled model
# ------------------------------------------------------------

adj_net_area_pred <- get_standardized_gam_predictions(
  model = model_PFN3_scaling,
  data = plot_dat,
  focal_var = "TC_area",
  focal_values = TC_grid,

  # Must match the variable actually used in the GAM
  group_var = "stat_22q",

  # Use 0/1 if stat_22q is numeric
  group_values = c(0, 1),

  # Population-level prediction
  exclude_terms = "s(subclass)"
)

adj_net_area_pred$stat_22q <- adj_net_area_pred$group


# ------------------------------------------------------------
# Set plotting window based on BOTH fitted curves + CIs
#
# Keep your original equal x/y-range logic.
# ------------------------------------------------------------

fit_pad_frac <- 0.05

pred_x_min <- min(
  log(adj_net_area_pred$x),
  na.rm = TRUE
)

pred_x_max <- max(
  log(adj_net_area_pred$x),
  na.rm = TRUE
)

fit_y_min <- min(
  adj_net_area_pred$predicted,
  adj_net_area_pred$conf.low,
  na.rm = TRUE
)

fit_y_max <- max(
  adj_net_area_pred$predicted,
  adj_net_area_pred$conf.high,
  na.rm = TRUE
)

x_required_range <- pred_x_max - pred_x_min
y_required_range <- fit_y_max - fit_y_min

plot_range <- max(
  x_required_range,
  y_required_range
)

# Preserve your original choice:
# plot_range <- plot_range * (1 + 2 * fit_pad_frac)

x_center <- mean(
  c(pred_x_min, pred_x_max)
)

y_center <- mean(
  c(fit_y_min, fit_y_max)
)

x_min <- x_center - plot_range / 2
x_max <- x_center + plot_range / 2

y_min <- y_center - plot_range / 2
y_max <- y_center + plot_range / 2


# ------------------------------------------------------------
# Plot
# ------------------------------------------------------------

Fig <- ggplot() +

  # Raw observations
  geom_point(
    data = plot_dat,
    aes(
      x = log(TC_area),
      y = log(.data[[PFN_area]]),
      color = stat_22q_plot
    ),
    size = 1,
    alpha = 0.4
  ) +

  # 95% CI from pooled inferential model
  geom_ribbon(
    data = adj_net_area_pred,
    aes(
      x = log(x),
      ymin = conf.low,
      ymax = conf.high,
      fill = stat_22q,
      group = stat_22q
    ),
    alpha = 0.20,
    color = NA
  ) +

  # Population-standardized scaling curves
  geom_line(
    data = adj_net_area_pred,
    aes(
      x = log(x),
      y = predicted,
      color = stat_22q,
      group = stat_22q
    ),
    linewidth = 1.2
  ) +

  scale_color_manual(
    name = NULL,
    labels = c(
      "PNC",
      "22q11DS"
    ),
    values = c(
      "0" = "#4D4D4D",
      "1" = "#D55E00"
    )
  ) +

  scale_fill_manual(
    name = NULL,
    labels = c(
      "PNC",
      "22q11DS"
    ),
    values = c(
      "0" = "#4D4D4D",
      "1" = "#D55E00"
    )
  ) +

  labs(
    title = NULL,
    x = NULL,
    y = NULL
  ) +

  theme_classic() +

  theme(
    plot.title = element_text(
      size = 25,
      hjust = 0.5
    ),
    axis.text.x = element_text(
      size = 44.75,
      color = "black"
    ),
    axis.text.y = element_text(
      size = 44.75,
      color = "black"
    ),
    axis.title.x = element_text(size = 1),
    axis.title.y = element_text(size = 1),

    legend.position = "right",
    legend.text = element_text(size = 24)
  ) +

  coord_cartesian(
    xlim = c(x_min, x_max),
    ylim = c(y_min, y_max),
    clip = "on"
  ) +

  scale_x_continuous(
    breaks = c(11.8, 12, 12.2)
  ) +

  scale_y_continuous(
    breaks = c(9.4, 9.6, 9.8)
  )

print(Fig)


ggsave(
  paste0(
    dout,
    "/PNC_22q_PFN3_pooled_interaction_log_log_Group_scaling.png"
  ),
  plot = Fig,
  width = 21.5,
  height = 16,
  dpi = 600,
  units = "cm"
)

ggsave(
  paste0(
    dout,
    "/PNC_22q_PFN3_pooled_interaction_log_log_Group_scaling.pdf"
  ),
  plot = Fig,
  device = cairo_pdf,
  width = 21.5,
  height = 16,
  units = "cm"
)
```


## 22q status * sex interaction models
```{r}
dout <- "../../Results/22q_Group_Age/Sex_Interaction_Models_subclass"
dir.create(dout)

interX_sex_models <- list()

for (net in c(1:17)) {
  PFN_area <- paste0("PFN",net)
  interX_model <- gam(log(get(PFN_area)) ~stat_22q+log(TC_area)+sex+euler+median_fd_combined+stat_22q*sex+s(age,k=4)+s(subclass, bs = "re"),data=matched_all,method = "REML")
  print(tab_model(interX_model,dv.labels=c(paste0("PFN ",net, " Area")),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = paste0(dout,"/Group_22qxSex_euler_age_PFN_",net,"_REML_subclass.doc")))
  interX_sex_models[[net]] <- interX_model #store all models in list
}

```

# Save out betas and bonf p-vals of 22q * sex interaction term
```{r}
dout <- "../../Results/22q_Group_Age/Sex_Interaction_Models_subclass"

interX_sex_mod_results <- matrix(0,17,2)

for (net in c(1:17)) {
  net_model <- interX_sex_models[[net]]
  interX_sex_mod_results[net,1] <- summary(net_model)$p.table["stat_22q1:sexMale", "Estimate"]
  interX_sex_mod_results[net,2] <- summary(net_model)$p.table["stat_22q1:sexMale", "Pr(>|t|)"]
}

pvals_bonf <- p.adjust(interX_sex_mod_results[,2], method = "bonf")
#PFN_names <- c("PFN1", "PFN2", "PFN3", "PFN4", "PFN5", "PFN6", "PFN7", "PFN8", "PFN9", "PFN10", "PFN11", "PFN12", "PFN13", "PFN14", "PFN15", "PFN16", "PFN17")
interX_sex_bonf <-  data.frame(PFN = PFN_names, beta = interX_sex_mod_results[,1], pvals_bonf = pvals_bonf)

write_csv(interX_sex_bonf,paste0(dout,"/Group_22qxSex_interaction_summary_results_REML_bonf_netnames_subclass.csv"))
```


## 22q status * age interaction models
```{r}
dout <- "../../Results/22q_Group_Age/Age_Interaction_Models_subclass"
dir.create(dout)

matched_all$ord_stat_22q <- ordered(matched_all$stat_22q, levels = c("0","1")) # 0 (no 22q) will be the reference group
matched_all$log_TC_area <- log(matched_all$TC_area)
interX_age_models <- list()

for (net in c(1:17)) {
  PFN_area <- paste0("PFN",net)
  interX_model <- gam(log(get(PFN_area)) ~ord_stat_22q+log_TC_area+sex+euler+median_fd_combined+s(age,k=4)+s(age,by=ord_stat_22q,k=4)+s(subclass, bs = "re"),data=matched_all,method = "REML")
  print(tab_model(interX_model,dv.labels=c(paste0("PFN ",net, " Area")),digits=2,digits.p=2,show.se=TRUE,show.stat=TRUE,string.stat = "t",string.se = "Std. Error",show.intercept=TRUE,show.ci = FALSE, p.adjust="none",p.style="scientific", file = paste0(dout,"/Group_22qxAge_euler_age_PFN_",net,"_REML_subclass.doc")))
  interX_age_models[[net]] <- interX_model #store all models in list
}
```


# Save out bonf p-vals of 22q * age interaction term
```{r}
dout <- "../../Results/22q_Group_Age/Age_Interaction_Models_subclass"

interX_age_mod_results <- matrix(0,17,2)

for (net in c(1:17)) {
  net_model <- interX_age_models[[net]]
  interX_age_mod_results[net,1] <- summary(net_model)$s.table["s(age):ord_stat_22q1", "F"]
  interX_age_mod_results[net,2] <- summary(net_model)$s.table["s(age):ord_stat_22q1", "p-value"]
}

pvals_bonf <- p.adjust(interX_age_mod_results[,2], method = "bonf")
#PFN_names <- c("PFN1", "PFN2", "PFN3", "PFN4", "PFN5", "PFN6", "PFN7", "PFN8", "PFN9", "PFN10", "PFN11", "PFN12", "PFN13", "PFN14", "PFN15", "PFN16", "PFN17")
interX_age_bonf <-  data.frame(PFN = PFN_names, F_stat = interX_age_mod_results[,1], pvals_bonf = pvals_bonf)

write_csv(interX_age_bonf,paste0(dout,"/Group_22qxAge_interaction_summary_results_REML_bonf_netnames_subclass.csv"))
```

# Visualize 22q * age interaction
```{r}

# ============================================================
# PFN 9: pooled age x diagnosis interaction
# ============================================================

net <- 9

model_PFN9 <- interX_age_models[[net]]


# ------------------------------------------------------------
# Use EXACT dataset used to fit the model
# ------------------------------------------------------------

age_plot_dat <- matched_all


# ------------------------------------------------------------
# Common observed age support between groups
# ------------------------------------------------------------

PNC_age_range <- range(
  age_plot_dat$age[age_plot_dat$stat_22q == 0],
  na.rm = TRUE
)

del22q_age_range <- range(
  age_plot_dat$age[age_plot_dat$stat_22q == 1],
  na.rm = TRUE
)

age_min_common <- max(
  PNC_age_range[1],
  del22q_age_range[1]
)

age_max_common <- min(
  PNC_age_range[2],
  del22q_age_range[2]
)

age_grid <- seq(
  age_min_common,
  age_max_common,
  length.out = 100
)


# ------------------------------------------------------------
# Population-standardized predictions
# ------------------------------------------------------------

pred <- get_standardized_gam_predictions(
  model = model_PFN9,
  data = age_plot_dat,
  focal_var = "age",
  focal_values = age_grid,
  group_var = "ord_stat_22q",
  group_values = c("0", "1"),
  exclude_terms = "s(subclass)"
)


# Rename for plotting
pred$age <- pred$x
pred$ord_stat_22q <- pred$group


# ------------------------------------------------------------
# Back-transform from log area
# ------------------------------------------------------------

pred$raw_fitted <- exp(pred$predicted)
pred$raw_lower  <- exp(pred$conf.low)
pred$raw_upper  <- exp(pred$conf.high)


# ------------------------------------------------------------
# Plot
# ------------------------------------------------------------

Fig_age <- ggplot(
  pred,
  aes(
    x = age,
    y = raw_fitted / 1000,
    color = ord_stat_22q
  )
) +

  geom_ribbon(
    aes(
      ymin = raw_lower / 1000,
      ymax = raw_upper / 1000,
      fill = ord_stat_22q
    ),
    alpha = 0.15,
    color = NA
  ) +

  geom_line(
    linewidth = 1.2
  ) +

  scale_color_manual(
    name = NULL,
    labels = c(
      "PNC",
      "22q11DS"
    ),
    values = c(
      "0" = "#4D4D4D",
      "1" = "#D55E00"
    )
  ) +

  scale_fill_manual(
    name = NULL,
    labels = c(
      "PNC",
      "22q11DS"
    ),
    values = c(
      "0" = "#4D4D4D",
      "1" = "#D55E00"
    )
  ) +

  labs(
    title = NULL,
    x = NULL,
    y = NULL
  ) +

  theme_classic() +

  theme(
    plot.title = element_text(
      size = 25,
      hjust = 0.5
    ),
    axis.text.x = element_text(
      size = 44.75,
      color = "black"
    ),
    axis.text.y = element_text(
      size = 44.75,
      color = "black"
    ),
    axis.title.x = element_text(size = 1),
    axis.title.y = element_text(size = 1),

    legend.position = "right",
    legend.text = element_text(size = 24)
  )

print(Fig_age)


ggsave(
  "../../Results/22q_Group_Age/Age_Interaction_Models_subclass/PFN9_age_Group_interaction_standardized_rawscale_REML_subclass.png",
  plot = Fig_age,
  width = 18.5,
  height = 16,
  dpi = 600,
  units = "cm"
)

ggsave(
  "../../Results/22q_Group_Age/Age_Interaction_Models_subclass/PFN9_age_Group_interaction_standardized_rawscale__REML_subclass.pdf",
  plot = Fig_age,
  width = 18.5,
  height = 16,
  units = "cm",
  device = cairo_pdf
)

```